### 2013-05-21 Problems.tex
Actual questions to answer

\documentclass{article}
\usepackage{amsmath,amscd,amssymb,latexsym, amsfonts}
\usepackage{mathtools}
\usepackage{amsthm}

\theoremstyle{plain}
\newtheorem{iassumption}{Assumption}
\newtheorem{theorem}{Theorem}[section]
\newtheorem{conjecture}[theorem]{Conjecture}
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{corollary}[theorem]{Corollary}
\newtheorem{hypothesis}[theorem]{Hypothesis}
\newtheorem{assumption}[theorem]{Assumption}
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{question}[theorem]{Question}
\newtheorem{exercise}[theorem]{Exercise}
\newtheorem{statement}[theorem]{Statement}
\newtheorem{example}[theorem]{Example}

\theoremstyle{definition}
\newtheorem{definition}[theorem]{Definition}
\newtheorem{remark}[theorem]{Remark}

\DeclareMathOperator{\Gal}{Gal}
\DeclareMathOperator{\val}{val}
\DeclareMathOperator{\HH}{H}
\DeclareMathOperator{\Ad}{Ad}
\DeclareMathOperator{\Nm}{Nm}
\DeclareMathOperator{\Hom}{Hom}
\DeclareMathOperator{\Spec}{Spec}
\DeclareMathOperator{\Res}{Res}
\DeclareMathOperator{\Fr}{Fr}
\DeclareMathOperator{\Tr}{Tr}
\DeclareMathOperator{\Ind}{Ind}
\DeclareMathOperator{\gen}{gen}

\DeclareMathOperator{\GL}{GL}
\DeclareMathOperator{\PGL}{PGL}
\DeclareMathOperator{\SL}{SL}

\newcommand{\mat}[4]{\left( \begin{array}{cc} {#1} & {#2} \\ {#3} & {#4}
\end{array} \right)}
\newcommand{\TT}{\mathcal{T}}
\newcommand{\C}{\mathcal{C}}
\newcommand{\RR}{\mathbb{R}}
\newcommand{\CC}{\mathbb{C}}
\newcommand{\CCx}{\mathbb{C}^\times}
\newcommand{\OK}{\mathcal{O}_K}
\newcommand{\OKn}{\mathcal{O}_{K_n}}
\newcommand{\pK}{\mathfrak{p}_K}
\newcommand{\pL}{\mathfrak{p}_L}
\newcommand{\OL}{\mathcal{O}_L}
\newcommand{\ZZ}{\mathbb{Z}}
\newcommand{\QQ}{\mathbb{Q}}
\newcommand{\Qp}{\mathbb{Q}_p}
\newcommand{\Gm}{\mathbb{G}_m}
\newcommand{\Lx}{L^\times}

\newcommand{\Weil}{\mathcal{W}}
\newcommand{\WD}{\mathcal{W}'}
\newcommand{\Lpack}{\mathcal{L}}
\newcommand{\Pgen}{P_G^{\gen}}
\newcommand{\bmu}{\boldsymbol\mu}
\newcommand{\mugen}{\bmu^{\gen}}

\newcommand{\la}{\langle}
\newcommand{\ra}{\rangle}

\newcommand{\invlim}[1]{\varprojlim_{#1}}
\newcommand{\Normalizer}[2]{\operatorname{N}_{#2}(#1)}

\begin{document}

\begin{enumerate}

\item For $K$ finite over $\Qp$ and $G$ a unitary group over $K$ splitting over $E$, classify maximal tori in $G$ in terms of \'etale algebras over $E$ with involution.

\begin{conjecture}
They should correspond to \'etale algebras $F / E$ with involution $\sigma$ restricting to the nontrivial involution of $E / K$.  Write $T_F$ for the corresponding torus, which is restriction of scalars of the Norm 1 torus from $F$ to $F^\sigma$.
\end{conjecture}
\item Given $T_F$, which unitary groups does it embed into.

\begin{conjecture}
Given $\kappa \in F^\sigma$, we can construct a hermitian space from the form $\la x, y \ra = \Tr_{F/E}(\kappa \cdot x \sigma(y)$ for $x, y \in F$.  These are precisely the unitary groups into which $T_F$ embeds.
\end{conjecture}

\item What are the invariants of these forms that we've constructed?

\begin{conjecture}
Taking the discriminant of this form should induce a homomorphism from $(F^\sigma)^\times$ to $K^\times / \Nm_{E/K} E^\times$ with kernel $\Nm_{F/F^\sigma} F^\times$.  Have we actually normalized correctly to make this happen.
\end{conjecture}

\item From this description can we read off various properties of the torus: ramified vs unramified, anisotropic, character and cocharacter lattice....

\item Can we give both the cohomological and intrinsic formulation of these questions?

\item What is the global picture?  Are the local-global obstructions?

\item What about $\RR$?

\end{enumerate}

\end{document}

### 2013-05-21 Problems.tex
Some more questions

@@
 
-\item From this description can we read off various properties of the torus: ramified vs unramified, anisotropic, character and cocharacter lattice....
+\item From this description can we read off various properties of the torus: ramified vs unramified, anisotropic, character and cocharacter lattices, N\'eron model....
 
@@
 
+\item For anisotropic tori can you describe the reduction of the maximal compact containing this torus?
+
 \end{enumerate}

### 2013-05-28 Problems.tex
Added a bunch of preliminary work. Layed out our hopeful claims as propositions/theorems Added proofs of some of them.

@@
 \newtheorem{definition}[theorem]{Definition}
+\newtheorem{notation}[theorem]{Notation}
 \newtheorem{remark}[theorem]{Remark}
@@
 
+\section{Problems}
+
 \begin{enumerate}
@@
 
+\section{Tori and \'Etale Algebras}
+
+Let $T$ be a torus defined over $K$ and $\rho:T_K \rightarrow \GL(V_K)$ a $K$-rational algebraic representation of $T$ (one can and might as well assume $\rho$ is injective).
+
+Associated to this data there exists an \'etale algebra $E$ over $K$, inclusions $\rho'' : E \hookrightarrow End(V_K)$ and $\rho' : T \rightarrow T_E$ for which $\rho = \rho''\circ\rho'$.
+
+\begin{proposition}
+We have the following constructions of $E$:
+\begin{enumerate}
+\item Let $X$ denote the set of characters of $T$ appearing via the representation of $\rho$ over $\overline{K}$.
+This is a Galois set for the action of $\Gal(\overline{K}/K)$ hence defines a unique \'etale algebra $E$.
+\item Let $C = C_\rho(T)$ be the centralizer of the image of $\rho(T)$ in $End(V_K)$ (as a scheme over $K$).
+           Let $Z = Z(C_\rho(T))$ be the centre of $C$ (as a scheme over $K$).
+           Let $E = Z(K)$.
+\item If the characters $\chi$ appearing in $X$ are distinguished by their values on $K$ points then $E$ is the $K$-span in $End(V_K)$ of $\rho(T(K))$.
+\end{enumerate}
+\end{proposition}
+\begin{proof}
+That (2) and (3) give \'etale algebras follows from base change to the algebraic closure.
+That the algebra constructed by (3) is contained in that constructed by (2) is clear.
+The converse can be checked over the algebraic closure, using flatness and dimension considerations.
+
+The equivalence of (1) and (3) follows from the characterization of \'etale algebras by Galois descent.
+\end{proof}
+
+\begin{remark}
+If the size of $X$ equivalently the $K$-dimension of $E$ equals the $K$ dimension of $V_K$ then $V_K$ is a rank $1$ module over $E$ hence may be (non-canonically) identified with $E$.
+\end{remark}
+
+\subsection{Structures on $E$}
+
+The choice of representation $\rho$ determines structures on $E$.
+
+\begin{proposition}
+Let $B : V_K \times V_K \rightarrow K$ be a non-degenerate bilinear form preserved by the image of $\rho$ then the adjoint involution on $End(V_K)$ (relative to $B$) defines an involution $\sigma$ on $E$.
+Moreover, $T \rightarrow T_{E\sigma} \rightarrow T_E$ is a factorization of the map $\rho'$.
+\end{proposition}
+\begin{proof}
+Denote by $\sigma$ the adjoint involution on $End(V_K)$.
+We are given that $B(x,y) = B(\rho(t)x,\rho(t)y) = B(x,\sigma(\rho(t))\rho(t)y)$ for all $x$ and $y$.
+By the non-degeneracy of $B$ this implies $\sigma(\rho(t))\rho(t)$ is the identity and thus $\sigma(\rho(t)) = \rho(t)^{-1}$.
+Thus, $\sigma$ takes $T$ to $T$.
+by the naturality of the construction of $E$ above $\sigma$ takes $E$ to $E$.
+
+It is now clear that $\rho(T) \subset T_{E,\sigma}$.
+\end{proof}
+
+\begin{proposition}
+Let $A$ be an algebra over $K$ and suppose $V_K$ has the structure of an $A$-module.
+Suppose $\rho(T)$ embeds into $End_A(V_K)$ then $E\hookrightarrow End_A(V_K)$.
+
+Suppose $\rho(T)$ commutes with the action of $A$, then the image of $E$ commutes with the action of $A$.
+If moreover the $K$-dimension of $E$ equals that of $V$ this also gives $E$ the structure of an $A$-algebra.
+\end{proposition}
+\begin{proof}
+By naturality of construction if $\rho(T)$ acts by $A$ endomorphisms then so too does $E$.
+Likewise if $\rho(T)$ commutes with the action of $A$, then so too does $E$.
+
+Finally, if $K$-dimensions are equal, then by identifying $V_K$ with $E$ we have given $E$ the structure of an $A$-module.
+Since the $A$ and $E$ multiplication commute, we are giving $E$ the structure of an $A$-algebra.
+\end{proof}
+\begin{remark}
+The case of non-commutative $E$ is mostly relevant to inner forms of symplectic groups.
+In what follows we will assume $A$ is a commutative algebra over $K$.
+\end{remark}
+
+\begin{proposition}
+Let $A$ be a quadratic algebra over $K$. Suppose $V_K$ has the structure of an $A$-module, and $B : V_K \times V_K \rightarrow A$ is a non-degenerate Hermitian form.
+Suppose  $\rho(T)$ preserves $B$ then $E\hookrightarrow End_A(V_K)$, the image of $E$ commutes with the action of $A$,  $E$ has the structure of an $A$-algebra, and the involution on $E$ restricts to that on $A$.
+\end{proposition}
+\begin{proof}
+The only new statement here is that the involution on $E$ restricts to the involution on $A$.
+The involution on $E$ was induced by the adjoint from $B$. But the involution on $A$ is by construction the adjoint.
+\end{proof}
+\begin{remark}
+The $K$-algebra $E= A\times A$ has two meaningfully different $A$-algebra structures arising from the inclusions:
+\[ a \mapsto (a,a) \qquad \text{and}\qquad a\mapsto (a,\sigma(a)) \]
+once we impose an involution on $E$. The two cases are meaningfully distinguished by how the involution restricts to $A$.
+\end{remark}
+
+\subsection{Sources of Representations}
+
+Let $G$ be an algebraic group over $K$ and suppose $T \hookrightarrow G$.
+Then any representation $\rho$ of $G$ restricts to a representation $\rho$ of $T$.
+
+The structures imposed on $E_T$ by $\rho$ are determined by the representation of $G$ and not by $T$.
+
+\begin{example}
+Let $\rho:G \hookrightarrow \GL(V_K,B)$ be a representation preserving the bilinear form $B$ then for all tori $T$ in $G$, there exists an \'etale algebra with involution $(E,\sigma)$ and and inclusion $T \hookrightarrow T_{E,\sigma}$.
+
+This holds even if $T$ is a split torus in the split unitary group $G=GL_n$ and $\rho$ is the representation corresponding to the standard representation of the unitary group.
+\end{example}
+
+\begin{example}
+If the form $B$ above is Hermitian for an action of $A$ on $V_K$ then $E$ is an $A$-algebra with the involution on $E$ restricting to that on $A$.
+
+In the split case the algebra $A$ is $K\oplus K$.
+\end{example}
+
+\section{Forms preserved by $T_{E,\sigma}$}
+
+\subsection{Structures of the Forms}
+
+\begin{theorem}
+Suppose $B_1,B_2$ be bilinear (or Hermitian) forms on $E$ for which the adjoint maps $Ad_{B_1}$ and $Ad_{B_2}$ induce the same map $\sigma:E\rightarrow E$.
+That is $B_i(ex,y) = B_i(x,\sigma(e)y)$, ie, we are in the case where $T_{E,\sigma}$ preserves $B_1$ and $B_2$.
+Then, $B_1(x,y) = B_2(\lambda x,y)$.
+\end{theorem}
+\begin{proof}
+Both $B_1$ and $B_2$ induce isomorphism between $E$ and its K (resp. A)-linear dual.
+Hence, there exists a unique $\lambda\in E$ such that $B_1(1,y) = B_2(\lambda,y)$ for all $y\in E$.
+We have:
+\[ B_1(e,x) = B_1(1,\sigma(e)x) = B_2(\lambda,\sigma(e)x) = B_2(\lambda e,x). \]
+\end{proof}
+\begin{theorem}
+If in the above if $B_1$ and $B_2$ are symmetric then $\sigma(\lambda)=\lambda$.
+
+If in the above $B_1$ and $B_2$ are Hermitian then $\sigma(\lambda)=\lambda$.
+\end{theorem}
+\begin{proof}
+We have the following calculation:
+\[ B_2(\lambda y,x) = B_1(y,x) = B_1(x,y) = B_2(\lambda x,y) = B_2(x,\sigma(\lambda) y) = B_2(\sigma(\lambda)y,x) \]
+Alternatively:
+\[ B_2(\lambda y,x) = B_1(y,x) = \overline{B_1(x,y)} = B_2(\lambda x,y) = \overline{B_2(x,\sigma(\lambda) y)} = B_2(\sigma(\lambda)y,x) \]
+And this holds for all $x,y$.
+Hence, by the uniqueness of $\lambda$ from above, $\lambda=\sigma(\lambda)$.
+\end{proof}
+\begin{corollary}
+All the non-degenerate symmetric bilinear forms on $E$ are of the form:
+\[ Tr_{E/K}(\lambda x\sigma(y) \]
+All the non-degenerate Hermitan forms on $E$ are of the form:
+\[ Tr_{E/A}(\lambda x\sigma(y) \]
+where $\lambda \in E^\sigma$ is a unit.
+In both cases, the isomorphism class of the form depends only on $\lambda \in (E^\sigma)^\times/N_{E/E^\sigma}(E^\times)$.
+\end{corollary}
+
+\subsection{Invariants of Hermitian Forms}
+
+TODO - in this section we might benefit from renormalizing the form, in my experiance letting $\lambda' = \lambda/f'_z(z)$ where $z\in E^\sigma$ is such that $\sqrt{z}$ primitively generates $E$ over $K$ is a good choice.
+(Such $z$ exist outside characteristic $2$ when $E$ is a field, or $E$ is an \'etale algebra and $K$ infinite).
+
+\begin{notation}
+Given an \'etale algebra with involution $(E,\sigma)$ and $\lambda \in (E^\sigma)^\times$
+denote the Hermitian form:
+\[ H_{E,\sigma,\lambda} := Tr_{E/A}(\lambda x\sigma(y)) \]
+and the symmetric bilinear form:
+\[ B_{E,\sigma,\lambda} := Tr_{E/A}(\lambda x\sigma(y)). \]
+\end{notation}
+
+\begin{proposition}
+Let $H$ be any Hermitian form and denote:
+\[ B(x,y) = Tr_{A/K}(H(x,y)). \]
+Then:
+\begin{enumerate}
+\item The discriminant of $H$ (and the discriminant of $A$) determines the Hasse invariant of $B$. (The converse holds whenever $A$ is not split.)
+\item The discriminant of $A$ determines the discriminant of $B$.
+\item The signatures of $H$ (and the infinite ramification of $A$) determines the signatures of $B$. The converse holds if $A$ is ramified.
+\end{enumerate}
+In particular the invariants of $B$ are equivalent to those of $H$.
+\end{proposition}
+\begin{proof}
+TODO - complete sketch.
+
+Hasse invariant uses formulas from my paper (see also BCKM).
+
+discriminant is easy (but also in my thesis)
+
+signature is easy by checking cases.
+\end{proof}
+
+\begin{proposition}
+The Hasse invariant of $B_{E,\sigma,\lambda}$ is:
+\[ TODO \]
+\end{proposition}
+
+\begin{proposition}
+The discriminant of invariant of $H_{E,\sigma,\lambda}$ is:
+\[ TODO \]
+Moreover, the map:
+\[ (E^\sigma)^\times/N_{E/E^\sigma}(E^\times) \rightarrow K^\times/N_{A/K}(A^\times) \]
+is a homomorphism.
+\end{proposition}
+\begin{proof}
+TODO - complete sketch
+
+We know Hasse invariant of $B_{E,\sigma,\lambda}$, the same computation (plus small amount of extra work) lets us compute Hasse invariant of $Tr_{A/K}(dx_0^2 \oplus_i x_i^2)$.
+Both formulas should be in terms of the Hilbert symbol.
+
+Provided $E/E^\sigma$ (equiv $A/K$) not split the formula should tell us non-trivial $d$ come from non-trivial $\lambda$.
+
+Note that  $(E^\sigma)^\times/N_{E/E^\sigma}(E^\times)$ is $( K^\times/N_{A/K}(A^\times))^\ell$ where $\ell$ is the number of field factors of $E$.
+\end{proof}
+
+\begin{proposition}
+The signature of $H_{E,\sigma,\lambda}$ is:
+\[ TODO \]
+\end{proposition}
+
+\subsection{Existence of Forms}
+
+\begin{theorem}
+Given $H$ a Hermitian form and $(E,\sigma)$ an \'etale algebra with involution (of the second kind) over $A$.Then for all $p$ primes of $K$ there exists $\lambda_p \in E^\sigma$ with:
+\[ H_p \simeq H_{E_p,\sigma,\lambda_p} \]
+TODO - I am pretty sure there are no conditions, I haven't fully checked.
+\end{theorem}
+\begin{proof}
+TODO - complete sketch
+
+non-split Infinite places (use signature proposition)
+
+non-split finite places (use discriminant map proposition)
+
+Split places (trivial)
+\end{proof}
+
+\begin{theorem}
+TODO - phrasing
+
+There exists $\lambda_p$ locally everywhere if and only if there exists $\lambda_p$ globally.
+\end{theorem}
+\begin{proof}
+TODO - complete sketch (also check that this is true).
+
+Argument 1:
+
+The local global obstruction allowing $\lambda$ such that $B_{E,\sigma,\lambda} \simeq B$ does not exist because for any place $p$ where $A/K$ is innert, then for every field factor of $E$ we have $E/E^\sigma$ is innert, thus there is no local global obstruction.
+
+The equivalence of $B$'s and $H$'s should conclude the result.
+
+\bigskip
+Argument 2:
+
+Optimistically global class field theory has a name for what we are doing.
+We need a $\lambda$ with controlled number of positive/negative embeddings, asside from this we are trying to say that the map:
+\[ (E^\sigma)^\times/N_{E/E^\sigma}(E^\times) \rightarrow K^\times/N_{A/K}(A^\times) \]
+is surjective.
+So in total what we want is surjective when we appropriately restrict to `totally postive' elements.
+This sounds like a very standard CFT type problem, and since by Argument 1 this result should hold...
+this result should have been proven by someone else before now.
+\end{proof}
+
+\section{Properties of $T_{E,\sigma}$}
+
+\subsection{Anisotropic}
+
+\begin{proposition}
+The torus $T_{E,\sigma}$ is anisotropic if all the field factors of $E$ are $\sigma$-stable.
+\end{proposition}
+\begin{proof}
+TODO-
+\end{proof}
+
+\begin{example}
+Consider $E = A \times A$ where $\sigma$ acts on each factor.
+This has the structure of an $A$ algebra, where $\sigma$ restricts to $\sigma$, by the inclusion $A\hookrightarrow A\times A$:
+\[ a \mapsto (a,a) \]
+The torus $T_{E,\sigma}$ is anisotropic.
+
+\bigskip
+Consider $E = A \times A$ where $\sigma$ acts to interchange factors.
+Give this the structure of an $A$ algebra, where $\sigma$ restricts to $\sigma$, by the inclusion $A\hookrightarrow A\times A$:
+\[ a \mapsto (a,\sigma(a)) \]
+The torus $T_{E,\sigma}$ is not anisotropic.
+\end{example}
+
+\subsection{Unramified}
+
+\begin{proposition}
+The torus $T_{E,\sigma}$ is unramified if all the field factors of $E$ are unramified
+\end{proposition}
+\begin{proof}
+TODO-
+\end{proof}
+
+\subsection{``Relatively'' Unramified}
+
+Your special unramifiedness when $A/K$ was ramified.
+
+\section{Cohomology}
+
+This is stuff I don't recall super well, I think the following is roughly true, you might recall better than I.
+
+\begin{question}
+The set of pairs $(T,U)$ consisting of $T$ a maximal torus (up to rational conjugacy) of $U$ and $U$ a pure inner form of a unitary group are in bijection with:
+\[ H^1( \Gal(\overline{K}/K), N_{U_0}(T_0) ) \]
+\end{question}
+If $T_0$ is split this becomes:
+\[ H^1( \Gal(\overline{K}/K), W(U,T_0) ) \]
+
+\begin{question}
+The set of pure inner forms of $U$ containing a torus isomorphic to $T_0$ is in bijection with the kernel of the natural map:
+\[ H^1( \Gal(\overline{K}/K), N_{U_0}(T_0) ) \rightarrow H^1( \Gal(\overline{K}/K),N_{GL_n}(T_E )) \]
+\end{question}
+
+\begin{question}
+the set of maximal tori $T$ in $U_0$ (up to rational conjugacy) is in bijection with the kernel of the natural map:
+\[  H^1( \Gal(\overline{K}/K), N_{U_0}(T_0) ) \rightarrow H^1( \Gal(\overline{K}/K), U_0) \]
+\end{question}
+
+The above should somehow give us that:
+\begin{question}
+The forms of $T$ contained in $U$ are in bijection with:
+\[ H^1(\Gal(\overline{K}/K), W(U_0,T_0)^{\Gal(\overline{K}/K} ) \]
+\end{question}
+However this could plausibly require that $T_0$ be split or that $U_0$ is quasi-split.
+
 \end{document}

### 2013-05-31 Paper.tex
Moved the 'paper' to a seperate file, should probably be renamed. Otherwise mostly added todo messages about things we should think about.

--- 2013-05-28 Problems.tex
@@
 \usepackage{amsmath,amscd,amssymb,latexsym, amsfonts}
-\usepackage{mathtools}
+%\usepackage{mathtools}
 \usepackage{amsthm}
@@
 \DeclareMathOperator{\gen}{gen}
+\DeclareMathOperator{\End}{End}
 
@@
 
+\newcommand{\TODO}[1]{\textbf{TODO-#1}}
+
+\title{Algebraic Tori in Unitary Groups}
+\author{Andrew Fiori \& David Roe}
+
 \begin{document}
 
-\section{Problems}
+\maketitle
 
-\begin{enumerate}
+\begin{abstract}
+We give a characterization of the algebraic tori in unitary groups in terms of the structure of \`etale algebras with involution.
+We determine relavent properties, such as unramifiedness or anisotropicness, of the tori from the associated algebra.
+We discuss the implications on the structure of the building for the unitary group.
+We give a cohomological reinterpretation of the results.
+\end{abstract}
 
-\item For $K$ finite over $\Qp$ and $G$ a unitary group over $K$ splitting over $E$, classify maximal tori in $G$ in terms of \'etale algebras over $E$ with involution.
+\tableofcontents
 
-\begin{conjecture}
-They should correspond to \'etale algebras $F / E$ with involution $\sigma$ restricting to the nontrivial involution of $E / K$.
-Write $T_F$ for the corresponding torus, which is restriction of scalars of the Norm 1 torus from $F$ to $F^\sigma$.
-\end{conjecture}
-\item Given $T_F$, which unitary groups does it embed into.
+\section{Introduction}
 
-\begin{conjecture}
-Given $\kappa \in F^\sigma$, we can construct a hermitian space from the form $\la x, y \ra = \Tr_{F/E}(\kappa \cdot x \sigma(y)$ for $x, y \in F$.
-These are precisely the unitary groups into which $T_F$ embeds.
-\end{conjecture}
+The problem of giving a classification and/or characterization of algebraic tori in algebraic groups has several sources of motivation coming out of algebraic number theory.
+In particular it has applications in the the theory of automorphic forms, Shimura varieties and the Langlands conjectures.
+Moreover, the algebraic tori play a key role in the construction of the building associated to the group, and also in the classification of forms of algebraic groups.
+Beyond all this the question is natural from a theoretical point of view in the theory of algebraic groups.
 
-\item What are the invariants of these forms that we've constructed?
+\TODO{More Motivational nonsense}
 
-\begin{conjecture}
-Taking the discriminant of this form should induce a homomorphism from $(F^\sigma)^\times$ to $K^\times / \Nm_{E/K} E^\times$ with kernel $\Nm_{F/F^\sigma} F^\times$.
-Have we actually normalized correctly to make this happen.
-\end{conjecture}
+\TODO{References to important literature}
 
-\item From this description can we read off various properties of the torus: ramified vs unramified, anisotropic, character and cocharacter lattices, N\'eron model....
+\TODO{Summary of Layout}
 
-\item Can we give both the cohomological and intrinsic formulation of these questions?
+\section{Definitions, Notation and Background}
 
-\item What is the global picture?  Are the local-global obstructions?
-
-\item What about $\RR$?
-
-\item For anisotropic tori can you describe the reduction of the maximal compact containing this torus?
-
-\end{enumerate}
+\TODO{} Decide which of the following to define/give notations for, we probably don't need all of it. Some of it can be postponed until the sections where it is used.
+\begin{itemize}
+\item The setting is a base field $K$ taken to be a $p$-adic field or number field (should we notationally distinguish? I don't currently).
+\item We shall denote by $...$ the absolute Galois group of $K$.
+\item \'Etale algebras are... typically denoted by $E$.
+\item \'Etale algebras with involutions are...
+\item Algebraic Tori are... 
+\item Hermitian Spaces are ... their invariants over (local fields, global fields) are...
+\item Unitary groups are ... their invariants over (local fields, global fields) are...
+\item Quadratic Forms are ...their invariants over (local fields, global fields) are...
+\item Orthogonal Groups are ...their invariants over (local fields, global fields) are...
+\item Connections between orthogonal and unitary groups.
+\end{itemize}
 
@@
 
-Associated to this data there exists an \'etale algebra $E$ over $K$, inclusions $\rho'' : E \hookrightarrow End(V_K)$ and $\rho' : T \rightarrow T_E$ for which $\rho = \rho''\circ\rho'$.
+Associated to this data there exists an \'etale algebra $E$ over $K$, inclusions $\rho'' : E \hookrightarrow \End(V_K)$ and $\rho' : T \rightarrow T_E$ for which $\rho = \rho''\circ\rho'$.
 
@@
 This is a Galois set for the action of $\Gal(\overline{K}/K)$ hence defines a unique \'etale algebra $E$.
-\item Let $C = C_\rho(T)$ be the centralizer of the image of $\rho(T)$ in $End(V_K)$ (as a scheme over $K$).
+\item Let $C = C_\rho(T)$ be the centralizer of the image of $\rho(T)$ in $\End(V_K)$ (as a scheme over $K$).
            Let $Z = Z(C_\rho(T))$ be the centre of $C$ (as a scheme over $K$).
            Let $E = Z(K)$.
-\item If the characters $\chi$ appearing in $X$ are distinguished by their values on $K$ points then $E$ is the $K$-span in $End(V_K)$ of $\rho(T(K))$.
+\item If the characters $\chi$ appearing in $X$ are distinguished by their values on $K$ points then $E$ is the $K$-span in $\End(V_K)$ of $\rho(T(K))$.
 \end{enumerate}
@@
 \begin{proposition}
-Let $B : V_K \times V_K \rightarrow K$ be a non-degenerate bilinear form preserved by the image of $\rho$ then the adjoint involution on $End(V_K)$ (relative to $B$) defines an involution $\sigma$ on $E$.
+Let $B : V_K \times V_K \rightarrow K$ be a non-degenerate bilinear form preserved by the image of $\rho$ then the adjoint involution on $\End(V_K)$ (relative to $B$) defines an involution $\sigma$ on $E$.
 Moreover, $T \rightarrow T_{E\sigma} \rightarrow T_E$ is a factorization of the map $\rho'$.
@@
 \begin{proof}
-Denote by $\sigma$ the adjoint involution on $End(V_K)$.
+Denote by $\sigma$ the adjoint involution on $\End(V_K)$.
 We are given that $B(x,y) = B(\rho(t)x,\rho(t)y) = B(x,\sigma(\rho(t))\rho(t)y)$ for all $x$ and $y$.
@@
 Let $A$ be an algebra over $K$ and suppose $V_K$ has the structure of an $A$-module.
-Suppose $\rho(T)$ embeds into $End_A(V_K)$ then $E\hookrightarrow End_A(V_K)$.
+Suppose $\rho(T)$ embeds into $\End_A(V_K)$ then $E\hookrightarrow \End_A(V_K)$.
 
@@
 Let $A$ be a quadratic algebra over $K$. Suppose $V_K$ has the structure of an $A$-module, and $B : V_K \times V_K \rightarrow A$ is a non-degenerate Hermitian form.
-Suppose  $\rho(T)$ preserves $B$ then $E\hookrightarrow End_A(V_K)$, the image of $E$ commutes with the action of $A$,  $E$ has the structure of an $A$-algebra, and the involution on $E$ restricts to that on $A$.
+Suppose  $\rho(T)$ preserves $B$ then $E\hookrightarrow \End_A(V_K)$, the image of $E$ commutes with the action of $A$,  $E$ has the structure of an $A$-algebra, and the involution on $E$ restricts to that on $A$.
 \end{proposition}
@@
 
-\subsection{Sources of Representations}
+\subsection{Tori in Algebraic Groups}
 
@@
 
-The structures imposed on $E_T$ by $\rho$ are determined by the representation of $G$ and not by $T$.
+The structures imposed on $E_T$ by $\rho$ are determined more by the representation $\rho$ of $G$ and not directly by $T$.
+If $\rho$ is injective the consequence is that all tori (at least conjugate to $T$ over $\overline{K}$) in $G$ will have the same structures.
 
@@
 This holds even if $T$ is a split torus in the split unitary group $G=GL_n$ and $\rho$ is the representation corresponding to the standard representation of the unitary group.
+Ie, if the representation corresponds to the same vector in the $A_n$ root system.
 \end{example}
@@
 
-\subsection{Structures of the Forms}
+\subsection{Shape of the Forms}
 
@@
 
-TODO - in this section we might benefit from renormalizing the form, in my experiance letting $\lambda' = \lambda/f'_z(z)$ where $z\in E^\sigma$ is such that $\sqrt{z}$ primitively generates $E$ over $K$ is a good choice.
+\TODO - in this section we might benefit from renormalizing the form, in my experiance letting $\lambda' = \lambda/f'_z(z)$ where $z\in E^\sigma$ is such that $\sqrt{z}$ primitively generates $E$ over $K$ is a good choice.
 (Such $z$ exist outside characteristic $2$ when $E$ is a field, or $E$ is an \'etale algebra and $K$ infinite).
+
+\TODO - probably want a lemma about how, or perhaps explaining invariants of Hermitian forms.
+$(d,\delta_{A/K}) $ for all intents and purposes is $d \in K^\times/N_{A/K}(A^\times)$.
 
@@
 
-\begin{proposition}
+\TODO - in all the following the Witt invariant formula might be nicer
+
+\begin{proposition}\label{prop:Hasse}
+The Hasse invariant of $B_{E,\sigma,\lambda}$ is:
+\[ Cor_{E^\sigma/K}((-\lambda f_z'(z),z)(-1,-1)^{n(n-1)/2}...). \]
+\end{proposition}
+This is \TODO - cite
+
+\begin{proposition}\label{prop:InvariantRelations}
 Let $H$ be any Hermitian form and denote:
@@
 \begin{enumerate}
-\item The discriminant of $H$ (and the discriminant of $A$) determines the Hasse invariant of $B$. (The converse holds whenever $A$ is not split.)
+\item The discriminant of $H$ (and the discriminant of $A$) determines the Hasse invariant of $B$. (The converse holds meaningfully whenever $A$ is not split, and is trivial otherwise.)
 \item The discriminant of $A$ determines the discriminant of $B$.
-\item The signatures of $H$ (and the infinite ramification of $A$) determines the signatures of $B$. The converse holds if $A$ is ramified.
+\item The signatures of $H$ (and the infinite ramification of $A$) determines the signatures of $B$. (The converse holds meaningfully if $A$ is ramified, and is trivial otherwise.)
 \end{enumerate}
@@
 \begin{proof}
-TODO - complete sketch.
+\TODO - complete sketch.
 
-Hasse invariant uses formulas from my paper (see also BCKM).
+By using Proposition \ref{prop:Hasse} one can compute that the Hasse invariant of the form:
+\[ \tfrac{1}{2}\Tr_{A/K}(dx_0\sigma(y_0) + \sum x_i\sigma(y_i)) \]
+is \TODO - work out exact 
+\[ (d,\delta_{A/K})(-2\delta_{A/K},\delta_{A/K})^n(-\delta_{A/K},-\delta_{A/K})^{n(n-1)/2}... \]
+Conversely, it follows that:
+\[ (d,\delta_{A/K}) = Hasse (...). \]
+At all places where $A/K$ is not split, this determines $d$ in $K^\times/N_{A/K}(A^\times)$.
+At all places where $A/K$ is split, the norm map is surjective, and the discriminant is meaningless.
+\TODO - phrasing that tells us we just determined $d$ globally.
 
-discriminant is easy (but also in my thesis)
+By \TODO - cite the discriminant of the form $B$ is precisely
+\[ (-\delta_{A/K})^n. \]
 
-signature is easy by checking cases.
+For a real ramified place the signature of $B$ is precisely:
+\[ (2s,2r) \]
+where $(s,r)$ is the signature of $H$.
+For a real split place the signature of $B$ is precisely:
+\[ (n,n) \]
+whereas, $H$ has no meaningful signature (the algebra $A$ is $\RR\times \RR$) as $-1$ is a norm.
+
+For complex places there are no signatures in either case.
 \end{proof}
-
-\begin{proposition}
-The Hasse invariant of $B_{E,\sigma,\lambda}$ is:
-\[ TODO \]
-\end{proposition}
 
@@
 \begin{proof}
-TODO - complete sketch
+\TODO - complete sketch
 
-We know Hasse invariant of $B_{E,\sigma,\lambda}$, the same computation (plus small amount of extra work) lets us compute Hasse invariant of $Tr_{A/K}(dx_0^2 \oplus_i x_i^2)$.
-Both formulas should be in terms of the Hilbert symbol.
+Combining the results of Propositions \ref{prop:Hasse} and \ref{prop:InvariantRelations} we find that:
+\TODO - details
+\[ (d,\delta_{A/K}) =  Cor_{E^\sigma/K}((\lambda,z)) Cor_{E^\sigma/K}((-f'(z),z) (-1,-1)^{n(n-1)/2}...) ... \]
+Now, if $\delta_{A/K}$ is a square then so is $z$
 
@@
 \[ H_p \simeq H_{E_p,\sigma,\lambda_p} \]
-TODO - I am pretty sure there are no conditions, I haven't fully checked.
+\TODO - I am pretty sure there are no conditions, I haven't fully checked.
 \end{theorem}
 \begin{proof}
-TODO - complete sketch
+\TODO - complete sketch
 
@@
 \begin{theorem}
-TODO - phrasing
+\TODO - phrasing
 
@@
 \begin{proof}
-TODO - complete sketch (also check that this is true).
+\TODO - complete sketch (also check that this is true).
 
@@
 \begin{proof}
-TODO-
+\TODO-
+That the condition is necissary is reasonably clear, sufficiency is less obvious.
 \end{proof}
@@
 \begin{proof}
-TODO-
+\TODO-
 \end{proof}
@@
 
-\section{Cohomology}
+\section{The Building of the Unitary Group}
+
+\subsection{The reduction of $T_{E,\sigma}$}
+
+\section{Cohomological Reinterpretation}
 

### 2013-06-01 Paper.tex
add some more details

@@
 \DeclareMathOperator{\End}{End}
+\DeclareMathOperator{\Cor}{Cor}
 
@@
 \begin{notation}
-Given an \'etale algebra with involution $(E,\sigma)$ and $\lambda \in (E^\sigma)^\times$
-denote the Hermitian form:
-\[ H_{E,\sigma,\lambda} := Tr_{E/A}(\lambda x\sigma(y)) \]
+Given an \'etale algebra with involution $(E,\sigma)$ of dimension $2n$ and $\lambda \in (E^\sigma)^\times$ let $z\in E^\sigma$ be such that $\sqrt{z}$ primitively generates $E$ over $K$ and denote by $f'_z(X)$ its minimal polynomial.
+Define the Hermitian form:
+\[ H_{E,\sigma,\lambda} := \tfrac{1}{2}Tr_{E/A}\left(\lambda x\sigma(y)\right) \]
 and the symmetric bilinear form:
-\[ B_{E,\sigma,\lambda} := Tr_{E/A}(\lambda x\sigma(y)). \]
+\[ B_{E,\sigma,\lambda} := \tfrac{1}{2}Tr_{E/A}\left(\lambda x\sigma(y)\right). \]
 \end{notation}
@@
 \begin{proposition}\label{prop:Hasse}
+The disciminant of $B_{E,\sigma,\lambda}$ is:
+\[  (-1)^n\delta_{E/K}, \]
 The Hasse invariant of $B_{E,\sigma,\lambda}$ is:
-\[ Cor_{E^\sigma/K}((-\lambda f_z'(z),z)(-1,-1)^{n(n-1)/2}...). \]
+\[  \Cor_{E^\sigma/K}((\lambda (-1)^n f_z'(z), z)_{E^\sigma})\cdot(-1,-1)_K^{n(n-1)/2}.\] 
+The signature of $B_{E,\sigma,\lambda}$ at a place where $E$ is complex and $E^\sigma$ is totally real is:
+\[ 2(\#\lambda^+. \#\lambda^-) \]
+is twice the number of positive and negative embeddings of $\lambda$.
 \end{proposition}
-This is \TODO - cite
+This is \TODO{cite Thm 3.3, 3.8, 5.2 in my paper}.
 
@@
 \begin{proof}
-\TODO - complete sketch.
+By using Proposition \ref{prop:Hasse}, and noting that $A = K(\sqrt{-\delta_{A/K}})$ one can compute that the Hasse invariant of the forms:
 
-By using Proposition \ref{prop:Hasse} one can compute that the Hasse invariant of the form:
-\[ \tfrac{1}{2}\Tr_{A/K}(dx_0\sigma(y_0) + \sum x_i\sigma(y_i)) \]
-is \TODO - work out exact 
-\[ (d,\delta_{A/K})(-2\delta_{A/K},\delta_{A/K})^n(-\delta_{A/K},-\delta_{A/K})^{n(n-1)/2}... \]
+\TODO - notation for discriminants of hermitian forms
+\[\Tr_{A/K}(dx_0\sigma(y_0)) \qquad \text{and} \qquad \Tr_{A/K}(x_1\sigma(y_1)) \]
+are respectively:
+\[ (-d \delta_{A/K}, \delta_{A/K})_K = (d,\delta_{A/K}) \qquad \text{and}\qquad ( -\delta_{A/K}, \delta_{A/K})_K = 1. \]
+From this we quickly conclude that the Hasse invariant of:
+\[ \Tr_{A/K}\left(dx_0\sigma(y_0) + \sum x_i\sigma(y_i)\right) \]
+is precisely
+\[ (d,\delta_{A/K})(-1,-1)_K^{n(n-1)/2}(\delta_{A/K},-1)_K^{n(n-1)/2}.\]
 Conversely, it follows that:
-\[ (d,\delta_{A/K}) = Hasse (...). \]
+\TODO - Notation
+\[ (d,\delta_{A/K}) = ``Hasse''  (\delta_{A/K},-1)_K^{n(n-1)/2}(-1,-1)_K^{n(n-1)/2}. \]
 At all places where $A/K$ is not split, this determines $d$ in $K^\times/N_{A/K}(A^\times)$.
@@
 
-By \TODO - cite the discriminant of the form $B$ is precisely
+By Proposition \ref{prop:Hasse} the discriminant of the form $B$ is precisely
 \[ (-\delta_{A/K})^n. \]
@@
 \begin{proposition}
-The discriminant of invariant of $H_{E,\sigma,\lambda}$ is:
-\[ TODO \]
+The discriminant of $H_{E,\sigma,\lambda}$ satisfies:
+\[  (d,\delta_{A/K})_K =  \Cor_{E^\sigma/K}((\lambda (-1)^n f_z'(z), z)_{E^\sigma}) \cdot (\delta_{A/K},-1)_K^{n(n-1)/2}. \]
 Moreover, the map:
 \[ (E^\sigma)^\times/N_{E/E^\sigma}(E^\times) \rightarrow K^\times/N_{A/K}(A^\times) \]
+given by:
+\TODO{notation for hermitian discriminant}
+\[ \lambda \mapsto (-1)^{n(n-1)/2} D\left( \tfrac{1}{2}\Tr_{E/A}\left( \frac{(-1)^n\lambda}{f'_z(z)} x\sigma(y) \right)\right) \]
 is a homomorphism.
@@
 \TODO - details
-\[ (d,\delta_{A/K}) =  Cor_{E^\sigma/K}((\lambda,z)) Cor_{E^\sigma/K}((-f'(z),z) (-1,-1)^{n(n-1)/2}...) ... \]
+\[ (d,\delta_{A/K}) =  \Cor_{E^\sigma/K}((\lambda,z)) \Cor_{E^\sigma/K}((-f'(z),z) (-1,-1)^{n(n-1)/2}...) ... \]
 Now, if $\delta_{A/K}$ is a square then so is $z$
@@
 \begin{proposition}
-The signature of $H_{E,\sigma,\lambda}$ is:
-\[ TODO \]
+The signature of $H_{E,\sigma,\lambda}$ at a real place of $K$ ramified in $A$ is:
+\[ (\#\lambda^+,\#\lambda^-) \]
 \end{proposition}

### 2013-06-01 Paper.tex
some comments

@@
 \usepackage{amsthm}
+\usepackage{xypic}
 
@@
 \newcommand{\Lx}{L^\times}
+\newcommand{\fp}{\mathfrak{p}}
 
@@
 
-Provided $E/E^\sigma$ (equiv $A/K$) not split the formula should tell us non-trivial $d$ come from non-trivial $\lambda$.
+Provided $E/E^\sigma$ not split the formula should tell us non-trivial $d$ come from non-trivial $\lambda$.
 
-Note that  $(E^\sigma)^\times/N_{E/E^\sigma}(E^\times)$ is $( K^\times/N_{A/K}(A^\times))^\ell$ where $\ell$ is the number of field factors of $E$.
+Note that for a local field $(E^\sigma)^\times/N_{E/E^\sigma}(E^\times)$ is $( K^\times/N_{A/K}(A^\times))^\ell$ where $\ell$ is the number of field factors of $E$ which are $\sigma$-stable.
 \end{proof}
@@
 \[ H_p \simeq H_{E_p,\sigma,\lambda_p} \]
-\TODO - I am pretty sure there are no conditions, I haven't fully checked.
+if and only if there exists a field factor $E_i$ of $E$ which is $\sigma$ stable.
 \end{theorem}
@@
 
+\TODO{The more I think about the following the less I think I know}
 \begin{theorem}
@@
 
-There exists $\lambda_p$ locally everywhere if and only if there exists $\lambda_p$ globally.
+There exists $\lambda_p$ locally everywhere if and only if there exists $\lambda$ globally.
 \end{theorem}
@@
 
-The local global obstruction allowing $\lambda$ such that $B_{E,\sigma,\lambda} \simeq B$ does not exist because for any place $p$ where $A/K$ is innert, then for every field factor of $E$ we have $E/E^\sigma$ is innert, thus there is no local global obstruction.
+The local global obstruction allowing $\lambda$ such that $B_{E,\sigma,\lambda} \simeq B$ does not exist because for any place $\fp$ where $A/K$ is innert, then for every field factor of $E$ that is not globally split we should have $E_\fp/E_\fp^\sigma$ is innert, thus there is no local global obstruction.
 
@@
 this result should have been proven by someone else before now.
+I suspect it is basically an application of Hasses theorem on norms.
+
+We are trying to claim that in the following commutative diagram: 
+\[
+\xymatrix{
+(E^\sigma)^\times/N_{E/E^\sigma}(E^\times) \ar[r]^{(\cdot,z)} \ar[d]& H^2(E^\sigma, \pm 1) \ar[r] \ar[d]& \prod_{E \text{ not split}} H^2(E^\sigma_\fp,\pm 1) \ar[d]\\
+K^\times/N_{A/K}(A^\times) \ar[r]^{(\cdot,\delta_{A/K})} & H^2(K, \pm 1) \ar[r] & \prod_{A \text{ not split}} H^2(K_\fp,\pm 1) .
+}
+\]
+That an element in $K^\times/N_{A/K}(A^\times) $ is in the image of the left verticle map, provided its image is in the image of the right hand verticle map.
+
+Can it happen that $E/A$ is a field, $\sigma : E \rightarrow E$ restricts to $\sigma$ on $A$ and there exists a prime $p$ of $A$ and $\fp|p$ of $E$ such that $\sigma(\fp) \neq \fp$ but $\sigma(p) = p$?
+
 \end{proof}

### 2013-06-03 Paper.tex
Add in some more details of some arguments

--- 2013-06-01 Paper.tex
@@
 
-\begin{proposition}
+\begin{proposition}\label{prop:discrimmap}
 The discriminant of $H_{E,\sigma,\lambda}$ satisfies:
@@
 
-Provided $E/E^\sigma$ (equiv $A/K$) not split the formula should tell us non-trivial $d$ come from non-trivial $\lambda$.
+Provided $E/E^\sigma$ not split the formula should tell us non-trivial $d$ come from non-trivial $\lambda$.
 
-Note that  $(E^\sigma)^\times/N_{E/E^\sigma}(E^\times)$ is $( K^\times/N_{A/K}(A^\times))^\ell$ where $\ell$ is the number of field factors of $E$.
+Note that for a local field $(E^\sigma)^\times/N_{E/E^\sigma}(E^\times)$ is $( K^\times/N_{A/K}(A^\times))^\ell$ where $\ell$ is the number of field factors of $E$ which are $\sigma$-stable.
 \end{proof}
 
-\begin{proposition}
-The signature of $H_{E,\sigma,\lambda}$ at a real place of $K$ ramified in $A$ is:
+\begin{proposition}\label{prop:discrimmapsurjective}
+Let $K$ be $p$-adic fidle, $\RR$ or $\CC$ and fix $A$ a quadratic extension of $K$ (potentially split).
+Fix $(E,\sigma)$ an \'etale algebra with involution (of the second kind) over $A$.
+If $E$ is a field then the homomorphism of Proposition \ref{prop:discrimmap} is surjective.
+\end{proposition}
+\begin{proof}
+The corestriction map is injective for local fields, and we are in the setting where both groups are isomorphic to $\{\pm1\}$, it follows immediately that the map is also surjective.
+\end{proof}
+
+\begin{proposition}\label{prop:signature}
+Let $K$ be $\RR$ and $A$ be $\CC$.
+If $E \simeq \CC$ then
+The signature of $H_{E,\sigma,\lambda}$ is:
 \[ (\#\lambda^+,\#\lambda^-) \]
+If $E\simeq \CC\times\CC$ with $\sigma$ interchanging factors then the signature of $H_{E,\sigma,\lambda}$ is:
+\[ (1,1). \]
 \end{proposition}
@@
 \begin{theorem}
-Given $H$ a Hermitian form and $(E,\sigma)$ an \'etale algebra with involution (of the second kind) over $A$.Then for all $p$ primes of $K$ there exists $\lambda_p \in E^\sigma$ with:
-\[ H_p \simeq H_{E_p,\sigma,\lambda_p} \]
-\TODO - I am pretty sure there are no conditions, I haven't fully checked.
+Let $K$ be a $p$-adic field and fix $A$ a quadratic extension of $K$ (potentially split).
+Given $H$ a Hermitian form and $(E,\sigma)$ an \'etale algebra with involution (of the second kind) over $A$. Then there exists $\lambda \in E^\sigma$ with:
+\[ H \simeq H_{E,\sigma,\lambda} \]
+if and only if there exists a factor $E_i^\sigma$ of $E^\sigma$ over which the corresponding factor of $E_i$ is not split.
 \end{theorem}
 \begin{proof}
-\TODO - complete sketch
+If $A$ is split over $K$ then there is a unique Hermitian space and hence nothing to show.
 
-non-split Infinite places (use signature proposition)
+In this setting the cohomology groups and the corestriction map of Propostion \ref{prop:discrimmap} are products of those appearing in Proposition \ref{prop:discrimmapsurjective}.
+The map of Propostion \ref{prop:discrimmap} is thus surjective if the cohomology groups are non-trivial.
+This is the case precisely if at least one factor of $E_i$ over $E_i^\sigma$ is not split.
+\end{proof}
 
-non-split finite places (use discriminant map proposition)
+\begin{example}
+Fix a prime numbers $p_1,p_2$ and $p_3$ such that $\left(\tfrac{p_1}{p_3}\right) = 1$ and $\left(\tfrac{p_2}{p_3}\right) = -1$.
+Set $A=\QQ(\sqrt{p_2})$ with the unique non-trivial involution, and $E=\QQ(\sqrt{p_2},\sqrt{p_1p_2})$ with the unique involution extending $\sigma$ acting trivially on $\sqrt{p_1p_2}$.
+Then $A_{p_3} = \QQ_{p_3}(\sqrt{p_2})$ and $E_{p_3} \simeq A_{p_3} \times A_{p_3}$ with $\sigma$ interchanging factors.
+It follows that the torus $T_{E,\sigma}$ does not embed into any unitary group which is not quasi-split at $p_3$.
+\end{example}
 
-Split places (trivial)
+\begin{theorem}
+Let $K$ be $\RR$ or $\CC$ and fix $A$ a quadratic extension of $K$ (potentially split).
+Given $H$ a Hermitian form and $(E,\sigma)$ an \'etale algebra with involution (of the second kind) over $A$. Then there exists $\lambda \in E^\sigma$ with:
+\[ H \simeq H_{E,\sigma,\lambda} \]
+if and only if 
+\TODO - phrase signature conditions
+\end{theorem}
+\begin{proof}
+If $A$ is split over $K$ then there is a unique Hermitian space and hence nothing to show.
+This is the case unless $A=\CC$ and $K=\RR$. In this case $E$ is $\CC^n$, however some of the factors might be interchanged by $\sigma$.
+By Proposition \ref{prop:signature} the factors interchanged by $\sigma$ must contribute $(1,1)$ to the signature.
+Wheras those not interchanged contribute $(1,0)$ or $(0,1)$ depending on the choice of $\lambda$.
+From this we conclude the result.
+\end{proof}
+
+\begin{example}
+\TODO - A CM-field field $A$ and a complex field $E$ such that $E\otimes_\QQ \RR$ has factors interchanged by an involution.
+\end{example}
+
+\begin{lemma}\label{Lem:liftsigma}
+Let Let $K$ be a number field and fix $A$ a quadratic extension of $K$ (potentially split).
+Fix $(E,\sigma)$ an \'etale algebra with involution (of the second kind) over $A$.
+Write $E = E_s \times E_{ns}$ where $E_s \simeq E_s^\sigma \times E_s^\sigma$ and $\sigma$ interchanges factors and $E_{ns}$ is a product of $\sigma$-stable fields.
+There exists $\tilde{\sigma} \in \Gal(\overline{K}/K)$ inducing $\sigma$ on $E_{ns}$ (that is a unique $\tilde{\sigma}$ induces the involution on each factor.
+\end{lemma}
+\begin{proof}
+Write:
+\[ E_{ns} = \prod E_i \]
+and set $\tilde{E} = E_1^\sigma E_2^\sigma\ldots E_{n}^\sigma$ to be the composite field of all the fixed fields of the $E_i$.
+Notice that $E_i \simeq E_i^\sigma\otimes_K A \simeq E_i^\sigma A$.
+Now, $A$ and $\tilde{E}$ are algebraicly disjoint fields and for all $i$ there exists canonical embeddings of fields:
+\[ \xymatrix{ E_i \simeq E_i^\sigma\otimes_K A \ar@{^(->}[r]\ar@{-}[d] &  \tilde{E} \otimes_K A \simeq \tilde{E}A \ar@{-}[d] \\ 
+                      E_i^\sigma \ar@{^(->}[r]\ar@{-} & \tilde{E}.}
+ \]
+The field $\tilde{E}A$ has a unique involution $\tilde{\sigma}$ such that $(\tilde{E}A)^{\tilde{\sigma}} = \tilde{E}$.
+Since $E_i^{\tilde{\sigma}} = E_i^\sigma$ this involution restricts to $\sigma$ on the image of $E_i$.
+Finally, $\tilde{\sigma}$ lifts to an element of $\Gal(\overline{K}/K)$, giving us the claim.
 \end{proof}
@@
 \begin{theorem}
-\TODO - phrasing
-
-There exists $\lambda_p$ locally everywhere if and only if there exists $\lambda_p$ globally.
+Let $K$ be a number field and fix $A$ a quadratic extension of $K$ (potentially split).
+Given $H$ a Hermitian form and $(E,\sigma)$ an \'etale algebra with involution (of the second kind) over $A$. Then there exists $\lambda \in E^\sigma$ with:
+\[ H \simeq H_{E,\sigma,\lambda} \]
+if and only if there exists $\lambda_\fp$ for all localizations $\fp$ of $K$ (both archimedian and non-archimedian).
 \end{theorem}
@@
 \TODO - complete sketch (also check that this is true).
+\TODO - need to distinguish primes of $K$, $A$ and $E$.
 
-Argument 1:
+Write $E^\sigma = \prod_{i=1}^n E^\sigma_i$.
+We have the following diagram:
+\[
+\xymatrix{
+(E^\sigma)^\times/N_{E/E^\sigma}(E^\times) \ar[r]^{(\cdot,z)} \ar[d]& H^2(E^\sigma, \pm 1) \ar[r] \ar[d]& \underset{E_{i,\fp} \text{ not split}}\oplus H^2(E^\sigma_{i,\fp},\pm 1) \ar[d]\\
+K^\times/N_{A/K}(A^\times) \ar[r]^{(\cdot,\delta_{A/K})} & H^2(K, \pm 1) \ar[r] & \underset{A_\fp \text{ not split}}\oplus H^2(K_\fp,\pm 1)
+}
+\]
+where the compositions of the horizontal maps are injective.
+We must show that an element in $K^\times/N_{A/K}(A^\times) $ is in the image of the left verticle map, provided its image is in the image of the right hand verticle map.
+We must do this in spite of the fact that the horizontal maps are not surjective.
 
-The local global obstruction allowing $\lambda$ such that $B_{E,\sigma,\lambda} \simeq B$ does not exist because for any place $p$ where $A/K$ is innert, then for every field factor of $E$ we have $E/E^\sigma$ is innert, thus there is no local global obstruction.
+The failure of surjectivity is captured by the following, the bottom map surjects onto the kernel of the map:
+\[ \underset{A_\fp \text{ not split}}\oplus H^2(K_\fp,\pm 1)  \rightarrow \{ \pm1\} \]
+given by $(x_\fp) \mapsto \prod x_\fp$. The top map surjects onto the kernel of the map:
+\[ \underset{E_{i,\fp} \text{ not split}}\oplus H^2(E_{i,\fp}^\sigma,\pm 1)  \rightarrow \{ \pm1\}^n \]
+given by $(x_{i,\fp}) \mapsto (\prod x_{1,\fp}, \ldots, \prod x_{n,\fp}) $.
 
-The equivalence of $B$'s and $H$'s should conclude the result.
+To complete the argument, it suffices to show that the kernel of the map:
+\[\underset{E_{i,\fp} \text{ not split}}\oplus H^2(E_{i,\fp}^\sigma,\pm 1)  \rightarrow \underset{A_\fp \text{ not split}}\oplus H^2(K_\fp,\pm 1) \]
+surjects onto the kernel of the map:
+\[ \{ \pm1\}^n \rightarrow \{ \pm1\}. \]
+To show this, it suffices to do this for a single fixed $\fp$ a prime of $K$.
+Fix $\fp$ any prime of $K$ where $\tilde{\sigma}$ of Lemma \ref{Lem:liftsigma} acts as Frobenius.
+Then for all $i$ there exists $\fp_i | \fp$ prime of $E_i^\sigma$ for which $E_{\fp_i,i}$ is non-split.
+It follows that $\oplus_i H^2(E_{\fp_i,i}^\sigma,\pm1)$ surjects onto $\{\pm 1\}^n$, thus this also holds for the larger group, and hence also for the kernels.
+\end{proof}
 
-\bigskip
-Argument 2:
+\begin{theorem}
+\TODO - summarize a pure global existance statement.
+\end{theorem}
 
-Optimistically global class field theory has a name for what we are doing.
-We need a $\lambda$ with controlled number of positive/negative embeddings, asside from this we are trying to say that the map:
-\[ (E^\sigma)^\times/N_{E/E^\sigma}(E^\times) \rightarrow K^\times/N_{A/K}(A^\times) \]
-is surjective.
-So in total what we want is surjective when we appropriately restrict to `totally postive' elements.
-This sounds like a very standard CFT type problem, and since by Argument 1 this result should hold...
-this result should have been proven by someone else before now.
-\end{proof}
+\begin{remark}
+\TODO - Can phrase this as: The reflex algebra splits the even clifford algebra + signature conditions.
+Is there a meaningfull interpretation of the clifford algebra in this context?
+Can we interpret it as telling us about a quaternioninc symplectic group embedding of the unitary group?
+\end{remark}
 

### 2014-03-22 Paper.tex
Added references file, made some changes

@@
 \usepackage{xypic}
+\usepackage{yfonts, mathrsfs}
 
@@
 
+\newcommand{\aK}{K}
+\newcommand{\gK}{\mathcal{K}}
+\newcommand{\lK}{\mathfrak{K}}
+\newcommand{\fK}{\textswab{K}}
+\newcommand{\aL}{L}
+\newcommand{\gL}{\mathcal{L}}
+\newcommand{\lL}{\mathfrak{L}}
+\newcommand{\fL}{\textswab{L}}
+\newcommand{\aE}{E}
+\newcommand{\gE}{\mathcal{E}}
+\newcommand{\lE}{\mathfrak{E}}
+\newcommand{\fE}{\textswab{E}}
+\newcommand{\aV}{V}
+\newcommand{\gV}{\mathcal{V}}
+\newcommand{\lV}{\mathfrak{V}}
+\newcommand{\fV}{\textswab{V}}
+
 \title{Algebraic Tori in Unitary Groups}
@@
 \begin{itemize}
+\item Explain our notation for fields and \'etale algebras: $\aK$, $\gK$, $\lK$, $\fK$, $\aL$, $\gL$, $\lL$, $\fL$, $\aE$, $\gE$, $\lE$, $\fE$, $\aV$, $\gV$, $\lV$, $\fV$.
 \item The setting is a base field $K$ taken to be a $p$-adic field or number field (should we notationally distinguish? I don't currently).
@@
 
-Let $T$ be a torus defined over $K$ and $\rho:T_K \rightarrow \GL(V_K)$ a $K$-rational algebraic representation of $T$ (one can and might as well assume $\rho$ is injective).
+Let $T$ be a torus defined over $\aK$, $\aV$ a vector space over $\aK$ and $\rho:T_\aK \rightarrow \GL(V)$ an injective $\aK$-rational algebraic representation of $T$.
 
-Associated to this data there exists an \'etale algebra $E$ over $K$, inclusions $\rho'' : E \hookrightarrow \End(V_K)$ and $\rho' : T \rightarrow T_E$ for which $\rho = \rho''\circ\rho'$.
+Associated to this data there exists an \'etale algebra $\aE$ over $\aK$, inclusions $\rho'' : \aE \hookrightarrow \End(V_K)$ and $\rho' : T \rightarrow T_E$ for which $\rho = \rho''\circ\rho'$.
 
@@
 and the symmetric bilinear form:
-\[ B_{E,\sigma,\lambda} := \tfrac{1}{2}Tr_{E/A}\left(\lambda x\sigma(y)\right). \]
+\[ B_{E,\sigma,\lambda} := \tfrac{1}{2}Tr_{E/K}\left(\lambda x\sigma(y)\right). \]
 \end{notation}

### 2014-03-22 references.tex
Added references file, made some changes

\documentclass{amsart}
\begin{document}

\begin{thebibliography}{9}

\bibitem Lawrence Morris, Some tamely ramified supercuspidal representations of symplectic groups, Proc. London Math. Soc. 63 (1991), no. 3, 519-551.

\bibitem Kazutoshi Kariyama, On Conjugacy Classes of Maximal Tori in Classical Groups.  Journal of Algebra, 125 (1989), 133-149

\bibitem Tignol et. al.  The Book of Involutions.

\bibitem Mark Reeder.  Elliptic Centralizers in Weyl Groups and their Coinvariant Representations.  Representation Theory, 15, (2011), pages 63-111.

\end{document}

### 2014-03-22 Paper.tex
Editing section 3.0

@@
 
+\newcommand{\GalKbK}{\Gamma_K}
+\newcommand{\Kb}{\overline{K}}
+
 \newcommand{\Weil}{\mathcal{W}}
@@
 \newcommand{\ra}{\rangle}
+
+%% Labeled items
+\makeatletter
+\newcommand{\labitem}[2]{
+\def\@itemlabel{\textbf{#1}}
+\item
+\def\@currentlabel{#1}\label{#2}}
+\makeatother
 
@@
 \item Explain our notation for fields and \'etale algebras: $\aK$, $\gK$, $\lK$, $\fK$, $\aL$, $\gL$, $\lL$, $\fL$, $\aE$, $\gE$, $\lE$, $\fE$, $\aV$, $\gV$, $\lV$, $\fV$.
-\item The setting is a base field $K$ taken to be a $p$-adic field or number field (should we notationally distinguish? I don't currently).
-\item We shall denote by $...$ the absolute Galois group of $K$.
-\item \'Etale algebras are... typically denoted by $E$.
-\item \'Etale algebras with involutions are...
+\item The setting is a base field $K$ taken to be a $p$-adic field or number field.
+\item We shall denote by $\GalKbK$ the absolute Galois group of $K$.
 \item Algebraic Tori are... 
+\item \'Etale algebras are... typically denoted by $E$.  Write $T_E$ for the $K$-torus $\Res_{E/K} \Gm$.
+\item \'Etale algebras with involutions are denoted by $(E, \sigma)$.
+Write $T_{E, \sigma}$ for the $K$-torus defined as the restriction from $E^\sigma$ to $K$ of the Norm 1 torus in $\Res_{E/E^\sigma} \Gm$.
 \item Hermitian Spaces are ... their invariants over (local fields, global fields) are...
@@
 
-Let $T$ be a torus defined over $\aK$, $\aV$ a vector space over $\aK$ and $\rho:T_\aK \rightarrow \GL(V)$ an injective $\aK$-rational algebraic representation of $T$.
+Let $T$ be a torus defined over $K$, $V$ a vector space over $K$ and $\rho : T \rightarrow \GL(V)$ an inclusion of $K$-groups.
+After diagonalizing the image of $\rho$ over $\Kb$, projecting onto each coordinate gives a finite set of characters of $T$; let $X$ denote the set of characters arising in this way.
 
-Associated to this data there exists an \'etale algebra $\aE$ over $\aK$, inclusions $\rho'' : \aE \hookrightarrow \End(V_K)$ and $\rho' : T \rightarrow T_E$ for which $\rho = \rho''\circ\rho'$.
+Associated to this data there exists an \'etale algebra $E$ over $K$, inclusions $\rho'' : E \hookrightarrow \End(V)$ and $\rho' : T \rightarrow T_E$ for which $\rho = \rho''\circ\rho'$.
 
-\begin{proposition}
-We have the following constructions of $E$:
+\begin{proposition} \label{prop:etale-construction}
+The following constructions produce isomorphic \'etale algebras $E$ over $K$:
 \begin{enumerate}
-\item Let $X$ denote the set of characters of $T$ appearing via the representation of $\rho$ over $\overline{K}$.
-This is a Galois set for the action of $\Gal(\overline{K}/K)$ hence defines a unique \'etale algebra $E$.
-\item Let $C = C_\rho(T)$ be the centralizer of the image of $\rho(T)$ in $\End(V_K)$ (as a scheme over $K$).
-           Let $Z = Z(C_\rho(T))$ be the centre of $C$ (as a scheme over $K$).
-           Let $E = Z(K)$.
-\item If the characters $\chi$ appearing in $X$ are distinguished by their values on $K$ points then $E$ is the $K$-span in $\End(V_K)$ of $\rho(T(K))$.
+\item \label{prop:etale-construction1} The set $X$ has an action of $\GalKbK$ and thus determines an \'etale algebra $E$.
+\item \label{prop:etale-construction2} Let $C = C_{\End(V)}(\rho(T))$ be the centralizer of $\rho(T)$ in $\End(V)$ and $Z$ be its center, both as schemes over $K$.
+Then $E = Z(K)$ is an \'etale algebra.
+\item \label{prop:etale-construction3} If $K$ is infinite, then $E$ can be taken as the $K$-span in $\End(V)$ of $\rho(T(K))$.
 \end{enumerate}
@@
 \begin{proof}
-That (2) and (3) give \'etale algebras follows from base change to the algebraic closure.
-That the algebra constructed by (3) is contained in that constructed by (2) is clear.
+That \eqref{prop:etale-construction2} and \eqref{prop:etale-construction3} give \'etale algebras follows from base change to the algebraic closure.
+That the algebra constructed by \eqref{prop:etale-construction3} is contained in that constructed by \eqref{prop:etale-construction2} is clear.
 The converse can be checked over the algebraic closure, using flatness and dimension considerations.
 
-The equivalence of (1) and (3) follows from the characterization of \'etale algebras by Galois descent.
+The equivalence of \eqref{prop:etale-construction1} and \eqref{prop:etale-construction3} follows from the characterization of \'etale algebras by Galois descent.
 \end{proof}
 
-\begin{remark}
-If the size of $X$ equivalently the $K$-dimension of $E$ equals the $K$ dimension of $V_K$ then $V_K$ is a rank $1$ module over $E$ hence may be (non-canonically) identified with $E$.
-\end{remark}
+From description \eqref{prop:etale-construction2}, we obtain inclusions $\rho'' : E \hookrightarrow \End(V)$ and $\rho' : T \rightarrow T_E$ which satisfy $\rho = \rho''\circ\rho'$.
+Furthermore, if $\dim_K E = \dim_K V$ then $\rho''$ gives $V$ the structure of a rank-$1$ $E$-module.
 

### 2014-03-23 Paper.tex
Edit Section 2
Add rough description of classification of Unitary groups.
Still need to add some references, which should eliminate need to prove
the details (check book of involutions)

@@
 
+\DeclareMathOperator{\Aut}{Aut}
 \DeclareMathOperator{\Gal}{Gal}
@@
 \item Unitary groups are ... their invariants over (local fields, global fields) are...
+
+For our purposes a unitary group is a simply connect group $G$ of type $A_n$.
+
+The forms of $G$ are in bijection with the elements of $H^1(\Gamma, \Aut(G))$.
+
+When $n>1$ the outer automorphism is a group of order $2$ and we have an exact sequence:
+\[ 1 \rightarrow   G^{adj} \rightarrow \Aut(G) \rightarrow \mu_2  \rightarrow 1 \]
+from which we obtain an exact sequence:
+\[ \ldots  H^1(\Gamma, G^{adj})  \rightarrow  H^1(\Gamma, \Aut(G)) \rightarrow  H^1(\Gamma, \mu_2) \rightarrow \ldots \]
+We conclude we can characterize forms of $G$ by invariants in $H^1(\Gamma, \mu_2)$ and $H^1(\Gamma, G^{adj})$.
+
+An element of $H^1(\Gamma, \mu_2)$ corresponds to a quadratic \'etale extension $E$ of $K$.
+More precisely it is the $n+1$ torsion of $T_{E,\sigma}$.
+We have an exact sequence:
+\[ \ldots \rightarrow H^1(\Gamma,G) \rightarrow H^1(\Gamma, G^{adj}) \rightarrow H^2(\Gamma, \mu_{n+1}^\xi) \rightarrow \ldots. \]
+A form of $G$ thus has an invariant in $H^2(\Gamma, mu_{n+1}^\xi)$.
+
+$H^2(\Gamma, \mu_{n+1}^\xi)$ fits into the exact sequence:
+\[ H^1(\Gamma, T_{E,\sigma}) \rightarrow H^2(\Gamma, mu_{n+1}^\xi) \rightarrow H^2(\Gamma, T_{E,\sigma}) \overset{[n+1]}\rightarrow H^2(\Gamma, T_{E,\sigma}). \]
+We are thus interested in the cohomology of $T_{E,\sigma}$.
+
+The exact sequence $1 \rightarrow T_{E,\sigma} \rightarrow T_E \rightarrow T_{E^\sigma} \rightarrow 1$ and Hilbert's Theorem 90 allow us to compute that 
+$H^1(\Gamma, T_{E,\sigma}) = k^\times/N_{E/k}(E^\times)$ and that $H^2(\Gamma, T_{E,\sigma})$ is the kernel of the corestriction map from the Brauer group of $E$ to that of $E^\sigma$.
+In particular we can now deduce that $H^2(\Gamma, \mu_{n+1}^\xi)$ corresponds to element a pair of an element of $\delta\in k^\times/(k^\times)^nN_{E/k}(E^\times)$ and a degree $n$ central simple algebra over $E$ in the $n$-torsion of the Brauer group which is only non-trivial at the places of $E$ over $K$ which split, and for places which split the algebra over one factor is isomorphic to the opposite algebra of that over the other.
+
+Finally, we must consider the group $H^1(\Gamma,G)$. As $G$ is simply connect, this is only non-trivial at the real places of $K$.
+In terms of real places, there are two cases to consider, when $E=\RR\times\RR$ then the $G$ is the automorphism group of a free module.
+As there are no forms of free modules, $H^1(\Gamma,G)$ is then trivial.
+If $E=\C$, then $G$ is the automorphism group of a Hermitian space and $H^1(\Gamma,G)$ classifies the Hermitian forms of the same discriminant as that defining $G$, over $\RR$ this means it classifies the signature.
+
+TODO --- Clarify how twisting determines the order in which invariants should be considered.
+
+Given a a collection of invariants, $E$, $A$, $\delta$, and signatures at real places of $K$ which ramify in $E$ we can construct the group $G$ as follows.
+By assumption $A$ can be given an involution $\sigma_A$ of restricting to $\sigma$ on $E$.
+Fix an element $J \in A^\sigma$ of reduced norm $\delta$ such that at each real place of $K$ which ramifies in $E$ the matrix for $J$ has $r$ positive eigenvalues and $s$ negative eigenvalues where $(r,s)$ is the signature at the real place.
+We may then define $G$ as:
+\[ G(R) = \{ g \in (A\otimes_K R)^\times \mid gJ\sigma_A(g) = J \} \]
+One may check that $G$ determines $E$, $A$, $\delta$ and the signatures uniquely when $n>1$.
+
+TODO --- REMARK ---
+In the case of $n=1$, we may perform the same constructions, however the group does not uniquely determine invariants $E$, $A$, $\delta$, and signatures.
+Indeed, there is no outer automorphism group, so the choice of $E$ is no longer an invariant.
+Exceptional isomorphisms of groups tell us that for $n=1$ the group $G$ is the spin group of a rank $3$ quadratic space.
+In odd rank the discriminant does not impact the isomorphism type of the orthogonal group.
+The discriminant of the quadratic space does still play a role in defining the Clifford algebra, in the same way it plays a role in defining a unitary group.
+The Witt invariant of the quadratic space is still an invariant and determines the algebra $A$.
+
 \item Quadratic Forms are ...their invariants over (local fields, global fields) are...

### 2014-03-23 Paper.tex
add some more background

--- 2014-03-22 Paper.tex
@@
 Write $T_{E, \sigma}$ for the $K$-torus defined as the restriction from $E^\sigma$ to $K$ of the Norm 1 torus in $\Res_{E/E^\sigma} \Gm$.
-\item Hermitian Spaces are ... their invariants over (local fields, global fields) are...
-\item Unitary groups are ... their invariants over (local fields, global fields) are...
+\item
+
+Fix a quadratic \'etale extension $E$ of $K$ and a free $E$-module $V$.
+A Hermitian structure on $V$ is a non-degenerate skew form $H : V\times V \rightarrow E$.
+We shall consider the group $U(H) = \Aut(V,H)$ and $SU(H) = \Aut(V,H,\det_E)$ where $\det_E$ refers to the $E$-module determinant on $V$.
+
+The forms of $V$ are in bijection with $H^1(\GalKbK, \Aut(V,H))$.
+We have an exact sequence:
+\[ 1 \rightarrow SU(H) \rightarrow U(H) \rightarrow T_{E,\sigma} \rightarrow 1. \]
+This induces an exact sequence:
+\[ \ldots \rightarrow H^1(\GalKbK,SU(H))  \rightarrow H^1(\GalKbK,U(H))  \rightarrow H^1(\GalKbK,T_{E,\sigma}) \rightarrow \ldots. \]
+We have an isomorphism $H^1(\GalKbK,T_{E,\sigma}) = K^\times/N_{E/K}(E^\times)$ and we shall refer to the associated invariant of $H$ as the discriminant.
+The group $SU(H)$ is simply connected, thus its cohomology is supported at the real places of $K$.
+When $E$ is split there are no forms, when $E=\C$ forms are classified by their signatures, that is the number of positive and negative eigenvalues for their Grahm matrix.
+
+We summarize the above with the following well known proposition.
+\begin{proposition}
+Fix a quadratic \'etale extension $E$ of $K$ and a free $E$-module $V$.
+Hermitian structures on $E$ are classified up to isomorphism by their discriminants $\delta\in K^\times/N_{E/K}(E^\times)$ and their signatures $(s_\nu,r_\nu)$ at real places of $K$ which ramify in $E$.
+Moreover, $\delta$ may be computed as the determinant of the Grahm matrix whereas $s_\nu$ and $r_\nu$ are respectively the number of positive and negative eigenvalues of hte Grahm matrix.
+\end{proposition}
+
+\item
+
+For our purposes a unitary group is a simply connect group $G$ of type $A_n$.
+
+The forms of $G$ are in bijection with the elements of $H^1(\GalKbK, \Aut(G))$.
+
+When $n>1$ the outer automorphism is a group of order $2$ and we have an exact sequence:
+\[ 1 \rightarrow   G^{adj} \rightarrow \Aut(G) \rightarrow \mu_2  \rightarrow 1 \]
+from which we obtain an exact sequence:
+\[ \ldots  H^1(\GalKbK, G^{adj})  \rightarrow  H^1(\GalKbK, \Aut(G)) \rightarrow  H^1(\GalKbK, \mu_2) \rightarrow \ldots \]
+We conclude we can characterize forms of $G$ by invariants in $H^1(\GalKbK, \mu_2)$ and $H^1(\GalKbK, G^{adj})$.
+
+An element of $H^1(\GalKbK, \mu_2)$ corresponds to a quadratic \'etale extension $E$ of $K$.
+More precisely it is the $n+1$ torsion of $T_{E,\sigma}$.
+We have an exact sequence:
+\[ \ldots \rightarrow H^1(\GalKbK,G) \rightarrow H^1(\GalKbK, G^{adj}) \rightarrow H^2(\GalKbK, \mu_{n+1}^\xi) \rightarrow \ldots. \]
+A form of $G$ thus has an invariant in $H^2(\GalKbK, mu_{n+1}^\xi)$.
+
+$H^2(\GalKbK, \mu_{n+1}^\xi)$ fits into the exact sequence:
+\[ H^1(\GalKbK, T_{E,\sigma}) \rightarrow H^2(\GalKbK, mu_{n+1}^\xi) \rightarrow H^2(\GalKbK, T_{E,\sigma}) \overset{[n+1]}\rightarrow H^2(\GalKbK, T_{E,\sigma}). \]
+We are thus interested in the cohomology of $T_{E,\sigma}$.
+
+The exact sequence $1 \rightarrow T_{E,\sigma} \rightarrow T_E \rightarrow T_{E^\sigma} \rightarrow 1$ and Hilbert's Theorem 90 allow us to compute that 
+$H^1(\GalKbK, T_{E,\sigma}) = k^\times/N_{E/k}(E^\times)$ and that $H^2(\GalKbK, T_{E,\sigma})$ is the kernel of the corestriction map from the Brauer group of $E$ to that of $E^\sigma$.
+In particular we can now deduce that $H^2(\GalKbK, \mu_{n+1}^\xi)$ corresponds to element a pair of an element of $\delta\in k^\times/(k^\times)^nN_{E/k}(E^\times)$ and a degree $n$ central simple algebra over $E$ in the $n$-torsion of the Brauer group which is only non-trivial at the places of $E$ over $K$ which split, and for places which split the algebra over one factor is isomorphic to the opposite algebra of that over the other.
+
+\begin{remark}
+It should be pointed out that the group $K^\times/(K^\times)^nN_{E/K}(E^\times)$ is trivial if either $n$ is odd or if $E = K\times K$ is split.
+\end{remark}
+
+Finally, we must consider the group $H^1(\GalKbK,G)$. As $G$ is simply connect, this is only non-trivial at the real places of $K$.
+In terms of real places, there are two cases to consider, when $E=\RR\times\RR$ then the $G$ is the automorphism group of a free module.
+ As there are no forms of free modules, $H^1(\GalKbK,G)$ is then trivial.
+If $E=\C$, then $G$ is the automorphism group of a Hermitian space and $H^1(\GalKbK,G)$ classifies the Hermitian forms of the same discriminant as that defining $G$, over $\RR$ this means it classifies the signature.
+
+Finally, we must consider the group $H^1(\GalKbK,G)$. As $G$ is simply connect, this is only non-trivial at the real places of $K$.
+More concretely, as $\Gal(\C/\RR)$ has a single element, $H^1(\GalKbK,G)$ is determined by $g\in G$ such that $g\sigma(g) = 1$ modulo $hg\sigma(h^{-1})$.
+TODO ---- do we actually want to explain this part concretely
+
+\begin{remark}
+Because we are dealing with non-abelian Galois cohomology when analyzing exact sequences we must twist by the cokernel elements before considering the structure of the kernel.
+It is for this reason that we must look at the invariants in the natural order $E$, $A$, $\delta$, signatures.
+\end{remark}
+
+Given a a collection of invariants, $E$, $A$, $\delta$, and $(s_\nu,r_\nu)$ we can construct the group $G$ as follows.
+By assumption $\sigma(A) \simeq A^{op}$ and thus $A$ can be given an involution $\sigma_A$ restricting to $\sigma$ on $E$.
+Fix an element $J \in A^\sigma$ of reduced norm $\delta$ such that at each real place of $K$ which ramifies in $E$ the matrix for $J$ has $r$ positive eigenvalues and $s$ negative eigenvalues where $(r,s)$ is the signature at the real place.
+We may then define $G$ as:
+\[ G(R) = \{ g \in (A\otimes_K R)^\times \mid gJ\sigma_A(g) = J \} \]
+One may check that $G$ determines $E$, $A$, $\delta$ and the signatures uniquely when $n>1$.
+
+\begin{remark}
+In the case of $n=1$, we may perform the same constructions, however the group does not uniquely determine invariants $E$, $A$, $\delta$, and signatures.
+Indeed, there is no outer automorphism group, so the choice of $E$ is no longer an invariant.
+Exceptional isomorphisms of groups tell us that for $n=1$ the group $G$ is the spin group of a rank $3$ quadratic space.
+In odd rank the discriminant does not impact the isomorphism type of the orthogonal group.
+The discriminant of the quadratic space does still play a role in defining the Clifford algebra, in the same way it plays a role in defining a unitary group.
+The Witt invariant of the quadratic space is still an invariant and determines the algebra $A$.
+
+It is worth remembering that choosing an $E$ and a discriminant is equivalent to choosing $A$.
+
+The following example illustrates that any two quadratic algebras have $2$-dimensional Hermitian spaces with isomorphic special unitary groups.
+\begin{example}
+Consider $L = K(\sqrt{d_1},\sqrt{d_2})$ with $\sigma$ the involution which acts as $-1$ on both $\sqrt{d_1}$ and $\sqrt{d_2}$.
+Then the maps $H_1 : L \times L \rightarrow K(\sqrt{d_1})$  $H_2 : L \times L \rightarrow K(\sqrt{d_2})$ given respectively by 
+$H_i(x,y) =  Tr_{L/K(\sqrt{d_i})}(\sqrt{\delta_1\delta_2}x\sigma(y))$ gives $L$ the structure of $K(\sqrt{d_i})$-Hermitian spaces.
+
+We may also consider the $K$-quadratic structure $B(x,y) = Tr_{L/K}(\sqrt{\delta_1\delta_2}x\sigma(y))$ and Symplectic structures $S_i(x,y) = Tr_{L/K}(\sqrt{\delta_i}x\sigma(y))$.
+Then we observe that $\Aut(H_i) = \Aut(B) \cap \Aut(S_i)$. With respect to the basis $\{1,\sqrt{\delta_1},\sqrt{\delta_2},\sqrt{\delta_1\delta_2}\}$ the forms have Gram matricies:
+\[ B \sim \begin{pmatrix} 0 & 0 & 0 & \delta_1\delta_2 \\ 0 & 0 &  \delta_1\delta_2 & 0 \\ 0 &  \delta_1\delta_2 & 0 & 0 \\  \delta_1\delta_2 & 0 & 0 & 0 \end{pmatrix} \]
+\[ S_1 \sim \begin{pmatrix} 0 & \delta_1 & 0 & 0 \\ -\delta_1 & 0 & 0 & 0 \\ 0 & 0 & 0 & \delta_1\delta_2 \\   0 & 0 & -\delta_1\delta_2 & 0  \end{pmatrix} \]
+\[ S_2  \sim \begin{pmatrix} 0 & 0 &  \delta_1&0 \\ 0 & 0 & 0 & \delta_1\delta_2 &  \\  -\delta_1 & 0  & 0 & 0 \\   0 & -\delta_1\delta_2 &0 & 0  \end{pmatrix} \]
+The matrix $\begin{pmatrix} 1 & 0 & 0 & 0 \\ 0 & 0 & 1 & 0 \\ 0 & 1 & 0 & 0 \\  0 & 0 & 0 & 1 \end{pmatrix} \in \Aut(B)$ transforms $S_1$ to $S_2$ and thus transforms $\Aut(H_1)$ to $\Aut(H_2)$
+\end{example}
+\end{remark}
+
 \item Quadratic Forms are ...their invariants over (local fields, global fields) are...

### 2014-03-23 Paper.tex
minor changes

@@
 Finally, we must consider the group $H^1(\GalKbK,G)$. As $G$ is simply connect, this is only non-trivial at the real places of $K$.
-In terms of real places, there are two cases to consider, when $E=\RR\times\RR$ then the $G$ is the automorphism group of a free module.
+In terms of real places, there are two cases to consider.
+If $E=\C$, then $G$ is the automorphism group of a Hermitian space and $H^1(\GalKbK,G)$ classifies the Hermitian forms of the same discriminant as that defining $G$, as above, over $\RR$ this means it classifies the signature.
+When $E=\RR\times\RR$ then the $G$ is the automorphism group of a free module.
  As there are no forms of free modules, $H^1(\GalKbK,G)$ is then trivial. 
-If $E=\C$, then $G$ is the automorphism group of a Hermitian space and $H^1(\GalKbK,G)$ classifies the Hermitian forms of the same discriminant as that defining $G$, over $\RR$ this means it classifies the signature.
-
-Finally, we must consider the group $H^1(\GalKbK,G)$. As $G$ is simply connect, this is only non-trivial at the real places of $K$.
-More concretely, as $\Gal(\C/\RR)$ has a single element, $H^1(\GalKbK,G)$ is determined by $g\in G$ such that $g\sigma(g) = 1$ modulo $hg\sigma(h^{-1})$.
-TODO ---- do we actually want to explain this part concretely
+TODO --- Find reference for this ----
 

### 2014-03-23 Paper.tex
reorganize a bit
Reorganize the description of forms of Hermitian forms and forms of
Unitary groups.

@@
 For our purposes a unitary group is a simply connect group $G$ of type $A_n$.
+We may construct such a group as follows.
+Fix the following:
+\begin{itemize}
+\item An quadratic \'etale algebra $E$ over $K$.
+\item A central simple $E$-algebra $F$ of degree $n$ with anti-involution $\sigma$ restricting to the non-trivial involution of $E$.
+\item An element $J\in F^\sigma$ of norm $\delta$ whose minimal polynomial at a real place $\nu$ of $K$ which ramifies in $E$ has $r_\nu$ positive roots and $s_\nu$ negative roots.
+\end{itemize}
+Define then $G$ to be the group scheme whose points over a $K$-algebra $R$ are given by:
+\[ G(R) = \{ g\in (F\otimes_K R)^\times \mid gJ\sigma(g) = J \}. \]
+
+We claim that all $G$ arrise this way, and that if $n>1$ then $G$ is uniquely determined by the invariants $(E,A,\delta, \left\vert r_\nu-s_\nu\right\vert)$ where $\delta \in K^\times/(K^\times)^nN_{E/K}(E^\times)$ subject only to the condition that $(-1)^{r_\nu-s_\nu}\delta$ is positive at all the real places of $K$ which ramify in $E$.
 
@@
 
-An element of $H^1(\GalKbK, \mu_2)$ corresponds to a quadratic \'etale extension $E$ of $K$.
-More precisely it is the $n+1$ torsion of $T_{E,\sigma}$.
+An element of $H^1(\GalKbK, \mu_2)$ corresponds to the quadratic \'etale extension $E$ of $K$.
+
+The center $\mu_{n+1}^\xi)$ of $G$ is the $n+1$ torsion of $T_{E,\sigma}$.
 We have an exact sequence:
@@
 We are thus interested in the cohomology of $T_{E,\sigma}$.
-
 The exact sequence $1 \rightarrow T_{E,\sigma} \rightarrow T_E \rightarrow T_{E^\sigma} \rightarrow 1$ and Hilbert's Theorem 90 allow us to compute that 
 $H^1(\GalKbK, T_{E,\sigma}) = k^\times/N_{E/k}(E^\times)$ and that $H^2(\GalKbK, T_{E,\sigma})$ is the kernel of the corestriction map from the Brauer group of $E$ to that of $E^\sigma$.
-In particular we can now deduce that $H^2(\GalKbK, \mu_{n+1}^\xi)$ corresponds to element a pair of an element of $\delta\in k^\times/(k^\times)^nN_{E/k}(E^\times)$ and a degree $n$ central simple algebra over $E$ in the $n$-torsion of the Brauer group which is only non-trivial at the places of $E$ over $K$ which split, and for places which split the algebra over one factor is isomorphic to the opposite algebra of that over the other.
+In particular we can now deduce that $H^2(\GalKbK, \mu_{n+1}^\xi)$ corresponds to element a pair of an element of $\delta\in k^\times/(k^\times)^nN_{E/k}(E^\times)$ and a degree $n$ central simple algebra $A$ over $E$ in the $n$-torsion of the Brauer group which is only non-trivial at the places of $E$ over $K$ which split, and for places which split the algebra over one factor is isomorphic to the opposite algebra of that over the other.
+
+It is precisely these algebras $A$ which admit non-trivial involutions acting non-trivially on there center.
+Indeed, in this setting we have that $A \otimes_{E,\sigma} E \simeq A^{op}$, that is if we twist the underlying $E$ algebra structure of $A$ then the resulting algebra is isomorphic to the opposite algebra of $A$ as an $E$-algebra.
+Let $\tau$ be the composition of the maps $A \rightarrow A \otimes_{E,\sigma} E \simeq A^{op} \rightarrow A$.
+This is an anti-involution on $A$, and as the map $A \rightarrow A \otimes_{E,\sigma} E $ is not a map of $E$-algebras (only of $K$-algebras) the map cannot act trivially on $E$.
+It must however preserve $E$ as this is the center of $A$.
+Thus $\tau$ restricts to $\sigma$ on $E$.
+
+TODO - ref book of involutions re conjugacy of these involutions
 
@@
 It should be pointed out that the group $K^\times/(K^\times)^nN_{E/K}(E^\times)$ is trivial if either $n$ is odd or if $E = K\times K$ is split.
+Further, for local fields at least one of $K^\times/(K^\times)^nN_{E/K}(E^\times)$ or $H^2(\GalKbK, T_{E,\sigma}) $ is trivial.
 \end{remark}
@@
 If $E=\C$, then $G$ is the automorphism group of a Hermitian space and $H^1(\GalKbK,G)$ classifies the Hermitian forms of the same discriminant as that defining $G$, as above, over $\RR$ this means it classifies the signature.
-When $E=\RR\times\RR$ then the $G$ is the automorphism group of a free module.
- As there are no forms of free modules, $H^1(\GalKbK,G)$ is then trivial. 
+When $E=\RR$ then $G$ is the automorphism group of a free module over a division algebra, there are no forms of these hence $H^1(\GalKbK,G)$ is trivial.
+
 TODO --- Find reference for this ----
@@
 
-Given a a collection of invariants, $E$, $A$, $\delta$, and $(s_\nu,r_\nu)$ we can construct the group $G$ as follows.
-By assumption $\sigma(A) \simeq A^{op}$ and thus $A$ can be given an involution $\sigma_A$ restricting to $\sigma$ on $E$.
-Fix an element $J \in A^\sigma$ of reduced norm $\delta$ such that at each real place of $K$ which ramifies in $E$ the matrix for $J$ has $r$ positive eigenvalues and $s$ negative eigenvalues where $(r,s)$ is the signature at the real place.
-We may then define $G$ as:
-\[ G(R) = \{ g \in (A\otimes_K R)^\times \mid gJ\sigma_A(g) = J \} \]
-One may check that $G$ determines $E$, $A$, $\delta$ and the signatures uniquely when $n>1$.
+One may check that $G$ determines $E$, $A$, $\delta$ and the signatures uniquely when $n>1$. Indeed, we may check this locally.
+When $G$ splits $E=K\times K$, when $E$ is quasi-split then $E$ is the unique quadratic extension over which $G$ splits.
+For places of $K$ which split in $E$, $G$ is precisely the norm one elements of the division algebra $A$, this uniquely determines $A$.
+For places which do not splite, $G$ is the special unitary group of a Hermitian form of discriminant $\delta$.
+The Hermitian form preserved by a special unitary group is unique up to scaling, $\delta$ respectively the signatures are the invariants of such forms.
 
 \begin{remark}
-In the case of $n=1$, we may perform the same constructions, however the group does not uniquely determine invariants $E$, $A$, $\delta$, and signatures.
+In the case of $n=1$, we may perform the same constructions, however the group does not uniquely determine invariants $E$, $A$, $\delta$, and signatures (if we fix $E$, the others are uniquely determined as above).
 Indeed, there is no outer automorphism group, so the choice of $E$ is no longer an invariant.

### 2014-03-24 Paper.tex
fix error

@@
 \begin{example}
-Consider $L = K(\sqrt{d_1},\sqrt{d_2})$ with $\sigma$ the involution which acts as $-1$ on both $\sqrt{d_1}$ and $\sqrt{d_2}$.
-Then the maps $H_1 : L \times L \rightarrow K(\sqrt{d_1})$  $H_2 : L \times L \rightarrow K(\sqrt{d_2})$ given respectively by 
-$H_i(x,y) =  Tr_{L/K(\sqrt{d_i})}(\sqrt{\delta_1\delta_2}x\sigma(y))$ gives $L$ the structure of $K(\sqrt{d_i})$-Hermitian spaces.
+Consider $\delta_1,\delta_2$ two elements of $K$.
+Let $A$ be the quaternion algebra $(\delta_1,\delta_2)$.
+Then $A$ is a $E_i=K(\sqrt{\delta_i})$ module for $i=1,2$ and a quadratic module over $K$.
+Hermitian  polarization of the norm form relative to the module structures makes $A$ into Hermitian spaces over both $E_1$ and $E_2$.
 
-We may also consider the $K$-quadratic structure $B(x,y) = Tr_{L/K}(\sqrt{\delta_1\delta_2}x\sigma(y))$ and Symplectic structures $S_i(x,y) = Tr_{L/K}(\sqrt{\delta_i}x\sigma(y))$.
-Then we observe that $\Aut(H_i) = \Aut(B) \cap \Aut(S_i)$. With respect to the basis $\{1,\sqrt{\delta_1},\sqrt{\delta_2},\sqrt{\delta_1\delta_2}\}$ the forms have Gram matricies:
-\[ B \sim \begin{pmatrix} 0 & 0 & 0 & \delta_1\delta_2 \\ 0 & 0 &  \delta_1\delta_2 & 0 \\ 0 &  \delta_1\delta_2 & 0 & 0 \\  \delta_1\delta_2 & 0 & 0 & 0 \end{pmatrix} \]
-\[ S_1 \sim \begin{pmatrix} 0 & \delta_1 & 0 & 0 \\ -\delta_1 & 0 & 0 & 0 \\ 0 & 0 & 0 & \delta_1\delta_2 \\   0 & 0 & -\delta_1\delta_2 & 0  \end{pmatrix} \]
-\[ S_2  \sim \begin{pmatrix} 0 & 0 &  \delta_1&0 \\ 0 & 0 & 0 & \delta_1\delta_2 &  \\  -\delta_1 & 0  & 0 & 0 \\   0 & -\delta_1\delta_2 &0 & 0  \end{pmatrix} \]
-The matrix $\begin{pmatrix} 1 & 0 & 0 & 0 \\ 0 & 0 & 1 & 0 \\ 0 & 1 & 0 & 0 \\  0 & 0 & 0 & 1 \end{pmatrix} \in \Aut(B)$ transforms $S_1$ to $S_2$ and thus transforms $\Aut(H_1)$ to $\Aut(H_2)$
+In either case we have that $A^1(R) = \{ g\in (A\otimes_K R)^\times \mid N_{A/K} = 1 \}$ acts by left multiplication on $A$ and preserves the norm form and thus both Hermitian forms.
+By base changing to $\overline{K}$ we redily verify that $A^1 = SU(H_i)$ for $i=1,2$.
+
+Over a local field the two isomorphism classes of $E_i$-Hermitian spaces arise from the two isomorphism classes of Quaternion algebra.
+Consequently both $E_1$ special unitary groups are isomorphic to $E_2$ special unitary groups.
+How isomorphism classes pair off is controlled by $(\delta_1,\delta_2)$.
 \end{example}

### 2014-04-03 Paper.tex
Add more background

@@
 \begin{abstract}
-We give a characterization of the algebraic tori in unitary groups in terms of the structure of \`etale algebras with involution.
+We give a characterization of the algebraic tori in unitary groups in terms of the structure of \'etale algebras with involution.
 We determine relavent properties, such as unramifiedness or anisotropicness, of the tori from the associated algebra.
@@
 \item We shall denote by $\GalKbK$ the absolute Galois group of $K$.
-\item Algebraic Tori are... 
-\item \'Etale algebras are... typically denoted by $E$.  Write $T_E$ for the $K$-torus $\Res_{E/K} \Gm$.
-\item \'Etale algebras with involutions are denoted by $(E, \sigma)$.
-Write $T_{E, \sigma}$ for the $K$-torus defined as the restriction from $E^\sigma$ to $K$ of the Norm 1 torus in $\Res_{E/E^\sigma} \Gm$.
-\item
+
+\end{itemize}
+
+\subsection{Tori and \'Etale Algebras}
+
+By an algebraic torus over $K$ we mean a group scheme $T$ over $K$ which is isomorphic to ${\Gm}_{\overline{K}}^n$ over $\overline{K}$.
+The automorphism group of $T$ over $\overline{K}$ is $GL_n(\ZZ)$ and thus forms of $T$ are classified by the cohomology set $H^1(\GalKbK,GL_n(\ZZ))$.
+
+By an \'etala algebra $E$ over the field $K$ we mean that $E$ is isomorphic to the direct product of (seperable) field extensions $E_i$ of $K$.
+Over the algebraic closure $\overline{K}$ of $K$ we have that $E\otimes_K \overline{K} \simeq \prod_\rho \overline{K}_\rho$ where $\rho \in \Hom(E,\overline{K})$.
+It is well known that forms of $E$ are in bijection with forms of the Galois set $\Hom(E,\overline{K})$ from which we obtain that \'etale algebras are classified by the Galois set $H^1(\GalKbK, \Sigma_n)$.
+
+Associated to an \'etale algebra $E$ is an algebraic torus which we shall denote by $T_E = \Res_{E/K} {\Gm}_E$.
+Its functor of points is given by:
+\[ T_E(R) = \{ g \in (E\otimes_K R)^\times \}. \]
+The splitting field of $T_E$ is the normal closure of $E$ and a basis for its character module is naturally identified with $\Hom(E,\overline{K})$.
+
+\begin{remark}
+All tori can be realized as subtori of $T_E$ (see \ref{TODO - forward ref}).
+\end{remark}
+
+By an \'etale algebra with involution $(E,\sigma)$, we mean an \'etale algebra $E$, and an automorphism of $E$ of order $2$ such that $E^\sigma$ the elements of $E$ fixed by $\sigma$ has half the dimension of $E$.
+This is equivalent to specifying the \'etale algebra $E^\sigma$, and a quadratic \'etale extension $E = E^\sigma[x]/(x^2-d)$ of $E^\sigma$ for an element $d\in (E^\sigma)^\times$.
+
+Associated to an \'etale algebra with involution $(E,\sigma)$ is an algebraic torus which we shall denote by $T_{E,\sigma} \subset T_E$.
+Its functor of points is:
+\[ T_{E,\sigma}(R) = \{ g \in (E\otimes_K R)^\times \mid g\sigma(g) = 1 \}. \]
+This torus sits in the exact sequence:
+\[ 1 \rightarrow  T_{E,\sigma} \rightarrow T_E \overset{N_{E/E^\sigma}}\rightarrow T_{E^\sigma} \rightarrow 1 \]
+
+\subsection{Hermitian Spaces}
 
@@
 
-\item
+\subsection{Unitary Groups}
 
@@
 \item An quadratic \'etale algebra $E$ over $K$.
-\item A central simple $E$-algebra $F$ of degree $n$ with anti-involution $\sigma$ restricting to the non-trivial involution of $E$.
+\item A central simple $E$-algebra $A$ of degree $n$ with anti-involution $\sigma$ restricting to the non-trivial involution of $E$.
 \item An element $J\in F^\sigma$ of norm $\delta$ whose minimal polynomial at a real place $\nu$ of $K$ which ramifies in $E$ has $r_\nu$ positive roots and $s_\nu$ negative roots.
@@
 Define then $G$ to be the group scheme whose points over a $K$-algebra $R$ are given by:
-\[ G(R) = \{ g\in (F\otimes_K R)^\times \mid gJ\sigma(g) = J \}. \]
+\[ G(R) = \{ g\in (A\otimes_K R)^\times \mid \sigma(g)Jg = J \text{ and } Nm(g) = 1 \}. \]
 
-We claim that all $G$ arrise this way, and that if $n>1$ then $G$ is uniquely determined by the invariants $(E,A,\delta, \left\vert r_\nu-s_\nu\right\vert)$ where $\delta \in K^\times/(K^\times)^nN_{E/K}(E^\times)$ subject only to the condition that $(-1)^{r_\nu-s_\nu}\delta$ is positive at all the real places of $K$ which ramify in $E$.
+We claim that all $G$ arise this way, and that if $n>1$ then $G$ is uniquely determined by the invariants $(E,A,\delta, \left\vert r_\nu-s_\nu\right\vert)$ where $\delta \in K^\times/(K^\times)^nN_{E/K}(E^\times)$ subject only to the condition that $(-1)^{r_\nu-s_\nu}\delta$ is positive at all the real places of $K$ which ramify in $E$.
 
@@
 
-TODO - ref book of involutions re conjugacy of these involutions
+\begin{remark}
+The choice of $J\in F^\sigma$ is equivalent to choosing the involution $\tau$.
+In particular, if we define $\tau'(x) = J\tau(x)J^{-1}$ then we obtain the same group using $\tau'$ and taking for $J$ the identity.
+
+Indeed, by \cite[Prop. 2.18]{The Book of Involutions TODO} all involutions on $A$ arise this way.
+Thus, the choice of $J$, can thus be thought of as choosing the involution.
+\end{remark}
 
@@
 
+TODO book of involutions 29.20 says this is trivial.
 TODO --- Find reference for this ----
@@
 
-\item Quadratic Forms are ...their invariants over (local fields, global fields) are...
-\item Orthogonal Groups are ...their invariants over (local fields, global fields) are...
-\item Connections between orthogonal and unitary groups.
+\subsection{Quadratic Spaces}
+
+Fix a free $K$-module $V$ of dimension $n$.
+In characteristic not $2$ to give a quadratic module structure on $K$ is equivalent to giving a non-degenerate symetric $K$-valued $K$-bilinear pairing $B$ on $V$.
+
+$O(B) = \Aut(V,B)$ and $SO(H) = \Aut(V,B,\det)$ where $\det$ refers to the $K$-module determinant on $V$.
+
+The forms of $V$ are in bijection with $H^1(\GalKbK, \Aut(V,O))$.
+We have an exact sequence:
+\[ 1 \rightarrow SO(B) \rightarrow O(B) \rightarrow \mu_2  \rightarrow 1. \]
+This induces an exact sequence:
+\[ \ldots \rightarrow H^1(\GalKbK,SO(B))  \rightarrow H^1(\GalKbK,O(B))  \rightarrow H^1(\GalKbK,\mu_2 ) \rightarrow \ldots. \]
+We have an isomorphism $H^1(\GalKbK, \{\pm1\}) = K^\times/(K^\times)^2$ and we shall refer to the associated invariant of $B$ as the discriminant.
+We thus have that the cohomology set $H^1(\GalKbK,SO(B))$ classifies forms with the same discriminant as $B$.
+The group $SO(B)$ has a simply connected cover $Spin(B)$, and there is an exact sequence:
+\[ \ldots \rightarrow H^1(\GalKbK,Spin(B))  \rightarrow H^1(\GalKbK,SO(B))  \rightarrow H^2(\GalKbK \mu_2 ).\]
+The group $H^2(\GalKbK,\{ \pm 1 \} )$ classifies quaternion algebras over $K$, we may thus associate to our form a quaternion algebra, which we shall refer to as the Hasse invariant.
+The set $H^1(\GalKbK,Spin(B)) $ then parameterizes forms with the same discriminant and Hasse invariant.
+As the group is simply connected, such forms are controlled at the real places of $K$, they are parametrized by the signature $(r_\nu,s_\nu)$.
+
+We summarize the above with the following well known proposition.
+\begin{proposition}
+Fix a free $K$-module $V$.
+Quadratic structures on $V$ are classified up to isomorphism by their discriminants $\delta \in K^\times/(K^\times)^2$, Hasse invariants $[A] \in  H^2(\GalKbK,\{ \pm 1 \} )$ and their signatures $(s_\nu,r_\nu)$ at real places of $K$ which ramify in $E$.
+Moreover, $\delta$ may be computed as the determinant of the Grahm matrix whereas $s_\nu$ and $r_\nu$ are respectively the number of positive and negative eigenvalues of the Grahm matrix in diagonal form.
+The Hasse invariant may be computed as $\prod_{i<j}(e_i,e_j)$ where $e_i,e_j$ are the eigenvalues for a Grahm matrix in diagonal form.
+\end{proposition}
+
+\begin{remark}
+There are several subtly different ways to define the Hasse (or Witt or Hasse-Witt) invariant, these typically differ by multiplication in the Brauer group by a constant depending on the discriminant.
+The one we have given is not equal to the coboundary map for the exact sequence above.
+\end{remark}
+
+\subsection{Orthogonal Groups}
+
+We shall be making use of orthogonal groups in even dimensions.
+For the purpose of this paper an even dimensional orthogonal group means a non-simply connected, non-adjoint group of type $D_n$.
+When $n\neq 4$ is even we additionally require that the kernel of the map from the simply connected cover be the same as the kernel of its vector representation.
+
+\begin{remark}
+When $n=1$ this group is $PSL_2$, when $n=2$ this group $SL_2\times SL_2/\pm1$, when $n=3$ this group is $PSL_4$.
+\end{remark}
+
+\begin{remark}
+When $n$ is even the center of the simply connected cover is $(\ZZ/2\ZZ)^2$ (possibly twisted), when it is odd it is $(\ZZ/4\ZZ)$ (possibly twisted), hence we only need the additional conditions clarifying which quotients we consider in teh case of $n$ even.
+In any case, as our quotient group is rational, the kernel from the simply connected cover is $\ZZ/2\ZZ$ (not twisted).
+\end{remark}
+
+When $n>1$ the outer automorphism group of such a group has order $2$.
+\begin{remark}
+Note that the triality automorphisms of $D_4$ does not descend to this quotient as the triality automorpism acts as the automorphism group of $(\ZZ/2\ZZ)^2$ on the center of the spin group.
+Thus no outer twist with non-trivial action via a three cycle contains rational elements in the center.
+\end{remark}
+
+We may construct the orthogonal groups as defined above as follows. Fix the following:
+\begin{itemize}
+\item A quaternion algebra $A$ over $K$ (we allow $M_2(K)$).
+\item Fix an orthogonal involution $\tau$ of $A$, for a quaternion algebra take $\tau(x) = i\sigma(x)i^{-1}$ for any $i\in A$ with $\sigma(i) = -i$, for $\sigma$ the standard involution of $A$, for the matrix algebra take $\tau$ to be the transpose.
+
+(An involution is orthogonal if the space of elements $x\in A$ with $\tau(x) = x$ has dimension $n(n+1)/2$ over $K$, otherwise it is symplectic and this dimension is $n(n-1)/2$ see \cite[2.6]{TODO the book of involutions}).
+\item An element $J \in M_{n}(A)^\times$ such that $J = \tau(J^t)$.
+Note that choosing $J$ is equivalent to the choice of orthogonal involution $\tau$.
 \end{itemize}
+Define then $\tilde{G}$ to be the group scheme whose points over a $K$-algebra $R$ are given by:
+\[ \tilde{G}(R) = \{ g\in (M_{n}(A) \otimes_K R)^\times \mid \tau(g^t)Jg = J  \}. \]
+Its connected component is the group scheme:
+\[ G(R) = \{ g\in (M_{n}(A) \otimes_K R)^\times \mid \tau(g^t)Jg = J  \text{ and } Nm(g) = 1 \}. \]
+We shall denote the simply connected cover by $\hat{G}$.
 
-\section{Tori and \'Etale Algebras}
+We claim that all orthogonal groups arise this way (note that $\hat{G}$ admits further forms in the case $n=4$).
+
+The outer automorphism group of such a group has order $2$.
+It is generated by an element of $\tilde{G}\setminus G$.
+We thus have an exact sequence:
+\[ 1 \rightarrow \mu_2 \rightarrow \tilde{G} \rightarrow \Aut(G) \rightarrow 1 \]
+from which we derive the exact sequence:
+\[\ldots \rightarrow H^1(\GalKbK,\mu_2) \rightarrow  H^1(\GalKbK, \tilde{G})  \rightarrow  H^1(\GalKbK, \Aut(G)) \rightarrow  H^2(\GalKbK, \mu_2)  \]
+We may thus associate to $G$ a quaternion algebra $A$, and an element of of the cohomology set $H^1(\GalKbK, \tilde{G})$ modulo the action of the cohomology group $H^1(\GalKbK,\mu_2)$.
+
+By \cite[29.16]{TODO - The book of involutions}
+the cohomology set $H^1(\Gamma, Isom(A,\tau)) = H^1(\Gamma,\tilde{G}) $ classifies the '$\tau$-symmetric elements of $A^\times$' up to change of basis.
+The action of $H^1(\GalKbK,\mu_2) $ is to rescale these by an element of $k^\times/(k^\times)^2$.
+\begin{remark}
+When $A$ is split, this is nothing other than the classification of quadratic forms up to rescaling as above.
+In even dimensions, this depends on the discriminant and the base change of the Hasse invariant to `discriminant' algebra.
+
+When $A$ is a quaternion algebra, the analysis proceeds as above, and we may still associate to $G$ a discriminant, a quaternion algebra and signature information. 
+As we shall not need it in the sequel, we omit the details, but remark that among other simplifications, $J$ can be taken to be diagonal, and the diagonal entries can be rescaled by $(K^\times)^2$
+\end{remark}
+
+\subsection{From Unitary Groups to Orthogonal Groups}
+
+In many cases unitary groups can be embedded into orthogonal groups, we shall only be making explicit use of this in the case where groups are associated to Hermitian and symmetric forms, however we present the more general situation.
+
+Fix the following data:
+\begin{itemize}
+\item An quadratic \'etale algebra $E$ over $K$ with involution $\sigma_E$.
+\item A quaternion algebra $A_0$ over $K$ with standard involution $\sigma_{A_0}$, then define $A = A_0\otimes_K E$ with an involution of the second kind $\sigma_A = \sigma_{A_0} \otimes \sigma_E$.
+(Note that all such $A$ arise uniquely this way see \cite[2.22]{TODO - book of involutions}).
+\item An element $J\in F^\sigma$ of norm $\delta$ whose minimal polynomial at a real place $\nu$ of $K$ which ramifies in $E$ has $r_\nu$ positive roots and $s_\nu$ negative roots.
+\end{itemize}
+Then define then $SU$ to be the associated unitary group whose points over a $K$-algebra $R$ are given by:
+\[ SU_J(R) = \{ g\in (A\otimes_K R)^\times \mid \sigma_A(g)Jg = J \text{ and } Nm(g) = 1 \}. \]
+
+Now, fix a $K$-division algebra $B$ with a fixed embedding of $E$ into $B$.
+Denote the standard involution on $B$ by $\sigma_{B}$ and define an orthogonal involution by $\tau_B(x) = y\sigma(x)y^{-1}$, where $y\in E$ has $\sigma_B(y) = -y$.
+
+Now define the algebra $C = A_0 \otimes_K B$, the involution $\sigma_C = \sigma_{A_0} \otimes \sigma_B$ is the standard involution and the involution $\tau_C = \sigma_{A_0} \otimes \tau_B$ is an orthogonal involution.
+Both $\sigma_C$ and $\tau_C$ restrict to $\sigma_A$ on the embedded image of $A$ in $C$.
+
+We may thus define the group schemes $SO_J$ and $SP$:
+\[ SO_J(R) =  \{ g\in (M_{n}(C) \otimes_K R)^\times \mid \tau_C(g^t)Jg = J  \} \]
+and
+\[ SP(R) =  \{ g\in (M_{n}(C) \otimes_K R)^\times \mid \sigma_C(g^t)Jg = J  \}. \]
+We redilly observe that $SU_J$ embedds naturally into both of these groups.
+\begin{remark}
+The group $SP$ is a symplectic group, its isomorphism class does not depend on $J$.
+\end{remark}
+
+\begin{remark}
+In the special case where $A_0$ and $B$ are split, so that $SU_J$ is the special unitary group of an $E$-valued Hermitian form $H$ associated to $J$ then
+$SO_J$ is the orthogonal group associated to the $K$-valued bilinear form $B(z_1,z_2) = \Tr_{E/K}(H(z_1,z_2))$ and the group $SP$ is the symplectic group associated to the symplectic form $S(z_1,z_2) = \Tr_{E/K}(H(yz_1,z_2))$.
+
+Note that given $SO_J$ or $SP$, and the $E$-module structure on the standard representations, the group $SU_J$ may be recovered.
+Note also that $U_J = SO_J \cap SP$.
+\end{remark}
+
+\section{\'Etale Algebras  associated to Tori in Algebra Groups}
 

### 2014-04-29 Paper.tex
Added a bit more

@@
 
+\TODO{Many well known results are still stated without proof here}
+
 \TODO{} Decide which of the following to define/give notations for, we probably don't need all of it. Some of it can be postponed until the sections where it is used.
@@
 \end{itemize}
+
+\subsection{Key Results in Galois Cohomology}
+
+We shall make frequent use of the following results of Galois cohomology.
+
+\TODO{Hasse Principle} The map from Global to local is injective.
+\TODO{Simply Connected Local Fields Thing} $H^1(G)$ is trivial if $G$ simply connected at a non-real local field
+\TODO{Simply connected real fields results} I feel someone has given an interpretation in terms of "indexes" of groups...
+
+optional:
+\TODO{H1 classifies torsors}
+\TODO{remarks re twisting}
+\TODO{H1 and H2 for relevant tori, restrictions of scalars and norms} (possibly in a later section?)
 
@@
 \item A central simple $E$-algebra $A$ of degree $n$ with anti-involution $\sigma$ restricting to the non-trivial involution of $E$.
-\item An element $J\in F^\sigma$ of norm $\delta$ whose minimal polynomial at a real place $\nu$ of $K$ which ramifies in $E$ has $r_\nu$ positive roots and $s_\nu$ negative roots.
+
+         Though unnecissary at this point, we note that for simplicity one is free to suppose that $\sigma$ has discriminant $1$ and is positive at all the real places of $K$ which ramify in $E$.
+         By the disciminant of $\sigma$ we mean the norm from $A$ to $K$ of an element $a$ with $\sigma(a)=-a$, by \cite[TODO]{book of involutions} this is well defined up to $N_{E/K}(E^\times)(K^\times)^n$.
+To say the involution is positive we mean that $a\sigma(a) \ge 0$.
+
+\item An element $J\in A^\sigma$ of norm $\delta$ whose minimal polynomial at a real place $\nu$ of $K$ which ramifies in $E$ has $r_\nu$ positive roots and $s_\nu$ negative roots.
 \end{itemize}
@@
 
-We claim that all $G$ arise this way, and that if $n>1$ then $G$ is uniquely determined by the invariants $(E,A,\delta, \left\vert r_\nu-s_\nu\right\vert)$ where $\delta \in K^\times/(K^\times)^nN_{E/K}(E^\times)$ subject only to the condition that $(-1)^{r_\nu-s_\nu}\delta$ is positive at all the real places of $K$ which ramify in $E$.
+\begin{theorem}
+All forms of $G$ arise this way.
+Moreover, if $n>1$ then $G$ is uniquely determined by the invariants $(E,A,\delta, \left\vert r_\nu-s_\nu\right\vert)$ where $\delta \in K^\times/(K^\times)^nN_{E/K}(E^\times)$ subject only to the condition that $(-1)^{r_\nu-s_\nu}\delta$ is positive at all the real places of $K$ which ramify in $E$.
+\end{theorem}
+\cite[TODO]{book of involutions}
+
+The cohomological interpretation of the above theorem is as follows:
 
@@
 Further, for local fields at least one of $K^\times/(K^\times)^nN_{E/K}(E^\times)$ or $H^2(\GalKbK, T_{E,\sigma}) $ is trivial.
+In the case of $H^2(\GalKbK, T_{E,\sigma}) $ trivial, the algebra $A$ is the matrix algebra, and the element of $K^\times/(K^\times)^nN_{E/K}(E^\times)$ is giving the discriminant of the involution, equivalently, the discriminant of the Hermitian space.
 \end{remark}
@@
 \begin{remark}
-There are several subtly different ways to define the Hasse (or Witt or Hasse-Witt) invariant, these typically differ by multiplication in the Brauer group by a constant depending on the discriminant.
-The one we have given is not equal to the coboundary map for the exact sequence above.
+There are several subtly different ways to define the Hasse (or Witt or Clifford) invariant, these typically differ by multiplication in the Brauer group by a constant depending on the discriminant.
+The one we have given (the standard definition of the Hasse invariant) is not equal to the coboundary map for the exact sequence above.
 \end{remark}
@@
 
-We claim that all orthogonal groups arise this way (note that $\hat{G}$ admits further forms in the case $n=4$).
+\begin{theorem}
+All forms of $G$ arise this way. (note that $\hat{G}$ admits further forms in the case $n=4$).
+\end{theorem}
+\cite[TODO]{book of involutions}
+
+The cohomological interpretation of this result is as follows:
 
@@
 When $A$ is split, this is nothing other than the classification of quadratic forms up to rescaling as above.
-In even dimensions, this depends on the discriminant and the base change of the Hasse invariant to `discriminant' algebra.
+In even dimensions, this depends on the discriminant and the base change of the Hasse invariant to the `discriminant' algebra.
 
-When $A$ is a quaternion algebra, the analysis proceeds as above, and we may still associate to $G$ a discriminant, a quaternion algebra and signature information. 
+When $A$ is a quaternion algebra, the analysis proceeds as above, and we may still associate to $G$ a discriminant, a central simple algebra (which is $2$-torsion if $n$ is even, and $4$-torsion when $n$ is odd) and signature information.
 As we shall not need it in the sequel, we omit the details, but remark that among other simplifications, $J$ can be taken to be diagonal, and the diagonal entries can be rescaled by $(K^\times)^2$
@@
 
+\subsection{Classification of Tori in Unitary Groups}
+
+\begin{theorem}
+Let $(E,A,\tau)$ be a triple consisting of a quadratic \'etale algebra $E$, a degree $n$ central simple algebra $A$ over $E$ with an involution $\tau$ of $A$ which restricts to the unique non-trivial involution on $E$.
+Let $U_{E,A,\tau}$ be the associated unitary group.
+Let $\delta_{\tau} \in K^\times/N_{E/K}(E^\times)$ denote the discriminant of $\tau$.
+
+Let $(E,M_n,\tilde{\tau})$ be the triple consisting of $E$, the matrix algebra of degree $n$ over $E$, and an involution $\tilde{\tau}$ of disciminant $\delta_{\tau}$ so that $U_{E,A,\tau}$ is the unitary group for the $E$-Hermitian space of discriminant $\delta_{\tau}$.
+
+The rational conjugacty classes of maximal tori in $U_{E,A,\tau}$ are naturally identified with a subset of those of $U_{E,M_n,\tilde{\tau}}$.
+The tori in $U_{E,M_n,\tilde{\tau}}$ are assicated to triples $(F,\sigma,\lambda)$, the rational conjugacy classes of tori in $U_{E,A,\tau}$ are precisely the subset for which $(F,\sigma)\hookrightarrow (A,\tau)$, equivalently, the subset for which $F$ splits $A$.
+
+The tori associated to $(F,\sigma,\lambda)$ in $U_{E,A,\tau}$ is the same as that in $U_{E,M_n,\tilde{\tau}}$ in particular they are $T_{F,\sigma}$, fixing an embedding $\rho : F \rightarrow A$, and an involution $\hat\tau$ of disciminant $1$ the conjugacy classes correspond to the image of $T_{F,\sigma}$ in $U_{E,A,\tau} \subset A$ where $U_{E,A,\tau}$ is defined comes from $\tau(x) = \rho(\lambda^{-1})\hat\tau(x)\rho(\lambda)$.
+
+The tori in $SU_{E,A,\tau}$ are the subtori $T_{F,\sigma,N_{F/E}}$.
+\end{theorem}
+\begin{proof}
+The proof is clear locally in terms of existence. 
+(Cite a result re embedding of algebras).
+
+Local existance -> global existance is easy, as $\lambda \in F$ places $\lambda \in A$ so as to allow us to define the involution, which has the correct local invariants and thus gives the correct unitary group.
+
+Local conjugacy class statement requires knowing conjugacy classes in the local non-split algebra setting. 
+The exact sequence $H^1(F) \rightarrow H^1(Aut(A,F)) \rightarrow H^1(Aut(F))$ tells us these are all conjugate.
+A direct argument of this claim would be nice.
+(Conjugacy of maximal \'etale sub-algebras of central simple algebras must be known).
+
+Global conjugacy class statement is then only claiming there are not more conjugacy classes than this, as global conjugacy would imply local conjugacy.
+It is "clear" they are conjugate if they differ by a norm of $F$, because this element can be used to "change" basis.
+(This is basically the Hasse principal in this case).
+\end{proof}
+
+\begin{remark}
+The cohomological interpretation of this result is as follows.
+
+We have shows already that rational conjugacy classes of tori in $U_{E,A,\tau}$ correspond to distinguished subalgebras with involution $(F,\sigma)$.
+Following the book of involutions (TODO-cite), we may classify pairs of $((E,A,\tau),(F,\sigma))$ by $H^1(Aut_K((E,A,\tau),(F,\sigma)))$.
+
+There is an exact sequence:
+\[ 1 \rightarrow T_{F,\sigma} \rightarrow Aut_K((E,A,\tau),(F,\sigma)) \rightarrow Aut_K(F,\sigma) \rightarrow 1 \]
+An element of $H^1(Aut_K(F,\sigma))$ specifies an \'etale algebra $F$, the element of $H^1(T_{F,\sigma})$ determines the conjugacy class.
+
+The elements of $H^1( Aut_K((E,A,\tau),(F,\sigma)))$ giving tori in $U_{E,A,\tau}$ is precisely the kernel of the map to $H^1(Aut_K((E,A,\tau))$.
+
+If we choose to work as in  (TODO cite reeder) with pure inner forms,
+We set $N$ to be the normalizer in $U_{E,A,\tau}$ of $T_{F,\sigma}$ and $Z$ be the center of $U_{E,A,\tau}$, we obtain an exact sequence:
+\[ 1 \rightarrow Z \rightarrow N \rightarrow Aut_K((E,A,\tau),(F,\sigma)) \rightarrow 1 \]
+That the tori in $U_{E,A,\tau}$ correspond to elements in the kernel of the map from $H^1(N)$ to $H^1(U_{E,A,\tau})$ is equivalent to the claim that there is a unique element of $H^1(Z)$ whose image is in this kernel so that we have an isomorphism from this kernel in $H^1(N)$ to the above kernel in $Aut_K((E,A,\tau),(F,\sigma))$.
+This claim about the elements of $H^1(Z)$ follows by observing that elements of $H^1(Z)$ are describing the discriminant of the unitary group.
+\end{remark}
+
 \section{Properties of $T_{E,\sigma}$}

### 2014-06-19 Paper.tex
More changing of phrasing, starting to add a section on unitary embedding into symplectic/orthogonal

--- 2014-03-24 Paper.tex
@@
 
-\DeclareMathOperator{\Aut}{Aut}
+\numberwithin{equation}{section}
+
 \DeclareMathOperator{\Gal}{Gal}
@@
 Write $T_{E, \sigma}$ for the $K$-torus defined as the restriction from $E^\sigma$ to $K$ of the Norm 1 torus in $\Res_{E/E^\sigma} \Gm$.
-\item
-
-Fix a quadratic \'etale extension $E$ of $K$ and a free $E$-module $V$.
-A Hermitian structure on $V$ is a non-degenerate skew form $H : V\times V \rightarrow E$.
-We shall consider the group $U(H) = \Aut(V,H)$ and $SU(H) = \Aut(V,H,\det_E)$ where $\det_E$ refers to the $E$-module determinant on $V$.
-
-The forms of $V$ are in bijection with $H^1(\GalKbK, \Aut(V,H))$.
-We have an exact sequence:
-\[ 1 \rightarrow SU(H) \rightarrow U(H) \rightarrow T_{E,\sigma} \rightarrow 1. \]
-This induces an exact sequence:
-\[ \ldots \rightarrow H^1(\GalKbK,SU(H))  \rightarrow H^1(\GalKbK,U(H))  \rightarrow H^1(\GalKbK,T_{E,\sigma}) \rightarrow \ldots. \]
-We have an isomorphism $H^1(\GalKbK,T_{E,\sigma}) = K^\times/N_{E/K}(E^\times)$ and we shall refer to the associated invariant of $H$ as the discriminant.
-The group $SU(H)$ is simply connected, thus its cohomology is supported at the real places of $K$.
-When $E$ is split there are no forms, when $E=\C$ forms are classified by their signatures, that is the number of positive and negative eigenvalues for their Grahm matrix.
-
-We summarize the above with the following well known proposition.
-\begin{proposition}
-Fix a quadratic \'etale extension $E$ of $K$ and a free $E$-module $V$.
-Hermitian structures on $E$ are classified up to isomorphism by their discriminants $\delta\in K^\times/N_{E/K}(E^\times)$ and their signatures $(s_\nu,r_\nu)$ at real places of $K$ which ramify in $E$.
-Moreover, $\delta$ may be computed as the determinant of the Grahm matrix whereas $s_\nu$ and $r_\nu$ are respectively the number of positive and negative eigenvalues of hte Grahm matrix.
-\end{proposition}
-
-\item
-
-For our purposes a unitary group is a simply connect group $G$ of type $A_n$.
-We may construct such a group as follows.
-Fix the following:
-\begin{itemize}
-\item An quadratic \'etale algebra $E$ over $K$.
-\item A central simple $E$-algebra $F$ of degree $n$ with anti-involution $\sigma$ restricting to the non-trivial involution of $E$.
-\item An element $J\in F^\sigma$ of norm $\delta$ whose minimal polynomial at a real place $\nu$ of $K$ which ramifies in $E$ has $r_\nu$ positive roots and $s_\nu$ negative roots.
-\end{itemize}
-Define then $G$ to be the group scheme whose points over a $K$-algebra $R$ are given by:
-\[ G(R) = \{ g\in (F\otimes_K R)^\times \mid gJ\sigma(g) = J \}. \]
-
-We claim that all $G$ arrise this way, and that if $n>1$ then $G$ is uniquely determined by the invariants $(E,A,\delta, \left\vert r_\nu-s_\nu\right\vert)$ where $\delta \in K^\times/(K^\times)^nN_{E/K}(E^\times)$ subject only to the condition that $(-1)^{r_\nu-s_\nu}\delta$ is positive at all the real places of $K$ which ramify in $E$.
-
-The forms of $G$ are in bijection with the elements of $H^1(\GalKbK, \Aut(G))$.
-
-When $n>1$ the outer automorphism is a group of order $2$ and we have an exact sequence:
-\[ 1 \rightarrow   G^{adj} \rightarrow \Aut(G) \rightarrow \mu_2  \rightarrow 1 \]
-from which we obtain an exact sequence:
-\[ \ldots  H^1(\GalKbK, G^{adj})  \rightarrow  H^1(\GalKbK, \Aut(G)) \rightarrow  H^1(\GalKbK, \mu_2) \rightarrow \ldots \]
-We conclude we can characterize forms of $G$ by invariants in $H^1(\GalKbK, \mu_2)$ and $H^1(\GalKbK, G^{adj})$.
-
-An element of $H^1(\GalKbK, \mu_2)$ corresponds to the quadratic \'etale extension $E$ of $K$.
-
-The center $\mu_{n+1}^\xi)$ of $G$ is the $n+1$ torsion of $T_{E,\sigma}$.
-We have an exact sequence:
-\[ \ldots \rightarrow H^1(\GalKbK,G) \rightarrow H^1(\GalKbK, G^{adj}) \rightarrow H^2(\GalKbK, \mu_{n+1}^\xi) \rightarrow \ldots. \]
-A form of $G$ thus has an invariant in $H^2(\GalKbK, mu_{n+1}^\xi)$.
-
-$H^2(\GalKbK, \mu_{n+1}^\xi)$ fits into the exact sequence:
-\[ H^1(\GalKbK, T_{E,\sigma}) \rightarrow H^2(\GalKbK, mu_{n+1}^\xi) \rightarrow H^2(\GalKbK, T_{E,\sigma}) \overset{[n+1]}\rightarrow H^2(\GalKbK, T_{E,\sigma}). \]
-We are thus interested in the cohomology of $T_{E,\sigma}$.
-The exact sequence $1 \rightarrow T_{E,\sigma} \rightarrow T_E \rightarrow T_{E^\sigma} \rightarrow 1$ and Hilbert's Theorem 90 allow us to compute that 
-$H^1(\GalKbK, T_{E,\sigma}) = k^\times/N_{E/k}(E^\times)$ and that $H^2(\GalKbK, T_{E,\sigma})$ is the kernel of the corestriction map from the Brauer group of $E$ to that of $E^\sigma$.
-In particular we can now deduce that $H^2(\GalKbK, \mu_{n+1}^\xi)$ corresponds to element a pair of an element of $\delta\in k^\times/(k^\times)^nN_{E/k}(E^\times)$ and a degree $n$ central simple algebra $A$ over $E$ in the $n$-torsion of the Brauer group which is only non-trivial at the places of $E$ over $K$ which split, and for places which split the algebra over one factor is isomorphic to the opposite algebra of that over the other.
-
-It is precisely these algebras $A$ which admit non-trivial involutions acting non-trivially on there center.
-Indeed, in this setting we have that $A \otimes_{E,\sigma} E \simeq A^{op}$, that is if we twist the underlying $E$ algebra structure of $A$ then the resulting algebra is isomorphic to the opposite algebra of $A$ as an $E$-algebra.
-Let $\tau$ be the composition of the maps $A \rightarrow A \otimes_{E,\sigma} E \simeq A^{op} \rightarrow A$.
-This is an anti-involution on $A$, and as the map $A \rightarrow A \otimes_{E,\sigma} E $ is not a map of $E$-algebras (only of $K$-algebras) the map cannot act trivially on $E$.
-It must however preserve $E$ as this is the center of $A$.
-Thus $\tau$ restricts to $\sigma$ on $E$.
-
-TODO - ref book of involutions re conjugacy of these involutions
-
-\begin{remark}
-It should be pointed out that the group $K^\times/(K^\times)^nN_{E/K}(E^\times)$ is trivial if either $n$ is odd or if $E = K\times K$ is split.
-Further, for local fields at least one of $K^\times/(K^\times)^nN_{E/K}(E^\times)$ or $H^2(\GalKbK, T_{E,\sigma}) $ is trivial.
-\end{remark}
-
-Finally, we must consider the group $H^1(\GalKbK,G)$. As $G$ is simply connect, this is only non-trivial at the real places of $K$.
-In terms of real places, there are two cases to consider.
-If $E=\C$, then $G$ is the automorphism group of a Hermitian space and $H^1(\GalKbK,G)$ classifies the Hermitian forms of the same discriminant as that defining $G$, as above, over $\RR$ this means it classifies the signature.
-When $E=\RR$ then $G$ is the automorphism group of a free module over a division algebra, there are no forms of these hence $H^1(\GalKbK,G)$ is trivial.
-
-TODO --- Find reference for this ----
-
-\begin{remark}
-Because we are dealing with non-abelian Galois cohomology when analyzing exact sequences we must twist by the cokernel elements before considering the structure of the kernel.
-It is for this reason that we must look at the invariants in the natural order $E$, $A$, $\delta$, signatures.
-\end{remark}
-
-One may check that $G$ determines $E$, $A$, $\delta$ and the signatures uniquely when $n>1$. Indeed, we may check this locally.
-When $G$ splits $E=K\times K$, when $E$ is quasi-split then $E$ is the unique quadratic extension over which $G$ splits.
-For places of $K$ which split in $E$, $G$ is precisely the norm one elements of the division algebra $A$, this uniquely determines $A$.
-For places which do not splite, $G$ is the special unitary group of a Hermitian form of discriminant $\delta$.
-The Hermitian form preserved by a special unitary group is unique up to scaling, $\delta$ respectively the signatures are the invariants of such forms.
-
-\begin{remark}
-In the case of $n=1$, we may perform the same constructions, however the group does not uniquely determine invariants $E$, $A$, $\delta$, and signatures (if we fix $E$, the others are uniquely determined as above).
-Indeed, there is no outer automorphism group, so the choice of $E$ is no longer an invariant.
-Exceptional isomorphisms of groups tell us that for $n=1$ the group $G$ is the spin group of a rank $3$ quadratic space.
-In odd rank the discriminant does not impact the isomorphism type of the orthogonal group.
-The discriminant of the quadratic space does still play a role in defining the Clifford algebra, in the same way it plays a role in defining a unitary group.
-The Witt invariant of the quadratic space is still an invariant and determines the algebra $A$.
-
-It is worth remembering that choosing an $E$ and a discriminant is equivalent to choosing $A$.
-
-The following example illustrates that any two quadratic algebras have $2$-dimensional Hermitian spaces with isomorphic special unitary groups.
-\begin{example}
-Consider $\delta_1,\delta_2$ two elements of $K$.
-Let $A$ be the quaternion algebra $(\delta_1,\delta_2)$.
-Then $A$ is a $E_i=K(\sqrt{\delta_i})$ module for $i=1,2$ and a quadratic module over $K$.
-Hermitian  polarization of the norm form relative to the module structures makes $A$ into Hermitian spaces over both $E_1$ and $E_2$.
-
-In either case we have that $A^1(R) = \{ g\in (A\otimes_K R)^\times \mid N_{A/K} = 1 \}$ acts by left multiplication on $A$ and preserves the norm form and thus both Hermitian forms.
-By base changing to $\overline{K}$ we redily verify that $A^1 = SU(H_i)$ for $i=1,2$.
-
-Over a local field the two isomorphism classes of $E_i$-Hermitian spaces arise from the two isomorphism classes of Quaternion algebra.
-Consequently both $E_1$ special unitary groups are isomorphic to $E_2$ special unitary groups.
-How isomorphism classes pair off is controlled by $(\delta_1,\delta_2)$.
-\end{example}
-\end{remark}
-
+\item Hermitian Spaces are ... their invariants over (local fields, global fields) are...
+\item Unitary groups are ... their invariants over (local fields, global fields) are...
 \item Quadratic Forms are ...their invariants over (local fields, global fields) are...
@@
 After diagonalizing the image of $\rho$ over $\Kb$, projecting onto each coordinate gives a finite set of characters of $T$; let $X$ denote the set of characters arising in this way.
-
-Associated to this data there exists an \'etale algebra $E$ over $K$, inclusions $\rho'' : E \hookrightarrow \End(V)$ and $\rho' : T \rightarrow T_E$ for which $\rho = \rho''\circ\rho'$.
 
@@
 
-From description \eqref{prop:etale-construction2}, we obtain inclusions $\rho'' : E \hookrightarrow \End(V)$ and $\rho' : T \rightarrow T_E$ which satisfy $\rho = \rho''\circ\rho'$.
-Furthermore, if $\dim_K E = \dim_K V$ then $\rho''$ gives $V$ the structure of a rank-$1$ $E$-module.
+From description \eqref{prop:etale-construction2}, we obtain inclusions $\rho_V : E \hookrightarrow \End(V)$ and $\rho_E : T \rightarrow T_E$ which satisfy $\rho = \rho_V \circ\rho_E$.
+Furthermore, if $\dim_K(E) = \dim_K(V)$ then $\rho_V$ gives $V$ the structure of a rank-$1$ $E$-module.
 
@@
 
-The choice of representation $\rho$ determines structures on $E$.
+Let $B : V \times V \rightarrow K$ be a non-degenerate bilinear form, and write $\sigma$ for the adjoint involution on $\End(V)$ relative to $B$.
 
 \begin{proposition}
-Let $B : V_K \times V_K \rightarrow K$ be a non-degenerate bilinear form preserved by the image of $\rho$ then the adjoint involution on $\End(V_K)$ (relative to $B$) defines an involution $\sigma$ on $E$.
-Moreover, $T \rightarrow T_{E\sigma} \rightarrow T_E$ is a factorization of the map $\rho'$.
+If $B$ is preserved by the image of $\rho$ then $\sigma$ induces an involution on $E$, which we will also denote $\sigma$.
+Moreover, the inclusion $\rho_E$ factors as $T \hookrightarrow T_{E, \sigma} \hookrightarrow T_E$.
 \end{proposition}
 \begin{proof}
-Denote by $\sigma$ the adjoint involution on $\End(V_K)$.
-We are given that $B(x,y) = B(\rho(t)x,\rho(t)y) = B(x,\sigma(\rho(t))\rho(t)y)$ for all $x$ and $y$.
-By the non-degeneracy of $B$ this implies $\sigma(\rho(t))\rho(t)$ is the identity and thus $\sigma(\rho(t)) = \rho(t)^{-1}$.
-Thus, $\sigma$ takes $T$ to $T$.
-by the naturality of the construction of $E$ above $\sigma$ takes $E$ to $E$.
+Suppose that $t \in T(K)$.  For all $x, y \in V$, we have $B(x,y) = B(\rho(t)x,\rho(t)y) = B(x,\sigma(\rho(t))\rho(t)y)$.  The non-degeneracy of $B$ implies that
+\begin{equation} \label{eq:Tstable}
+\sigma(\rho(t)) = \rho(t)^{-1},
+\end{equation}
+and thus $\sigma$ stabilizes $T(K)$.  By the naturality of the construction of $E$, the involution $\sigma$ must also stabilize $E$.
 
-It is now clear that $\rho(T) \subset T_{E,\sigma}$.
+The image of $T$ under $\rho_E$ lies within $T_{E,\sigma}$ by \eqref{eq:Tstable}.
 \end{proof}
 
+Let $A$ be a commutative $K$-algebra and that $V$ has the structure of an $A$-module.  Then $\End_A(V) \subseteq \End(V)$.
+
 \begin{proposition}
-Let $A$ be an algebra over $K$ and suppose $V_K$ has the structure of an $A$-module.
-Suppose $\rho(T)$ embeds into $\End_A(V_K)$ then $E\hookrightarrow \End_A(V_K)$.
 
-Suppose $\rho(T)$ commutes with the action of $A$, then the image of $E$ commutes with the action of $A$.
-If moreover the $K$-dimension of $E$ equals that of $V$ this also gives $E$ the structure of an $A$-algebra.
+\begin{enumerate}
+\item If $\rho(T) \subset \End_A(V)$, then $\rho_V(E) \subset \End_A(V)$.
+%\item If $\rho(T)$ commutes with the action of $A$, then so does $\rho_V(E)$.
+\item If $\dim_K(E) = \dim_K(V)$, then the action of $A$ on $V$ gives $E$ the structure of an $A$-algebra.
+\end{enumerate}
 \end{proposition}
 \begin{proof}
-By naturality of construction if $\rho(T)$ acts by $A$ endomorphisms then so too does $E$.
-Likewise if $\rho(T)$ commutes with the action of $A$, then so too does $E$.
+By naturality of construction, if $\rho(T)$ acts by $A$-endomorphisms, then so too does $\rho_V(E)$.
+%Likewise, if $\rho(T)$ commutes with the action of $A$, then so too does $\rho_V(E)$.
 
-Finally, if $K$-dimensions are equal, then by identifying $V_K$ with $E$ we have given $E$ the structure of an $A$-module.
-Since the $A$ and $E$ multiplication commute, we are giving $E$ the structure of an $A$-algebra.
+Moreover, if $\dim_K(E) = \dim_K(V)$, then any $E$-linear identification of $V$ with $E$ induces an $A$-module structure on $E$.
+Since $\rho_V(E)$ commutes with the action of $A$, $E$ is actually an $A$-algebra.
 \end{proof}
-\begin{remark}
-The case of non-commutative $E$ is mostly relevant to inner forms of symplectic groups.
-In what follows we will assume $A$ is a commutative algebra over $K$.
-\end{remark}
+%\begin{remark}
+%The case of non-commutative $E$ is mostly relevant to inner forms of symplectic groups.
+%In what follows we will assume $A$ is a commutative algebra over $K$.
+%\end{remark}
+
+Now suppose that $A$ be a quadratic algebra over $K$ and the assumptions of both of the previous propositions hold: $V$ has the structure of an $A$-module,  $B : V \times V \rightarrow A$ is a non-degenerate Hermitian form.
 
 \begin{proposition}
-Let $A$ be a quadratic algebra over $K$. Suppose $V_K$ has the structure of an $A$-module, and $B : V_K \times V_K \rightarrow A$ is a non-degenerate Hermitian form.
-Suppose  $\rho(T)$ preserves $B$ then $E\hookrightarrow \End_A(V_K)$, the image of $E$ commutes with the action of $A$,  $E$ has the structure of an $A$-algebra, and the involution on $E$ restricts to that on $A$.
+\begin{enumerate}
+\item If $B$ is preserved by the image of $\rho$ then $\rho(T) \subset \End_A(V)$ and thus $\rho_V(E) \subset \End_A(V)$.
+\item If $\dim_K(E) = \dim_K(V)$ then $E$ is an $A$-algebra and the involution on $E$ restricts to that on $A$.
+\end{enumerate}
 \end{proposition}
 \begin{proof}
-The only new statement here is that the involution on $E$ restricts to the involution on $A$.
+We need to prove that $\rho(T) \subset \End_A(V)$ and that the involution on $E$ restricts to the involution on $A$.
+\TODO{Prove the first claim}
 The involution on $E$ was induced by the adjoint from $B$. But the involution on $A$ is by construction the adjoint.
@@
 
+\section{Embeddings of unitary groups in symplectic and orthogonal groups}
+
+\begin{theorem}
+Suppose $H$ is a Hermitian space
+\end{theorem}
+
 \end{document}

### 2014-06-19 Paper.tex

--- 2014-04-29 Paper.tex
@@
 
+\numberwithin{equation}{section}
 \DeclareMathOperator{\Aut}{Aut}
@@
 
-Associated to this data there exists an \'etale algebra $E$ over $K$, inclusions $\rho'' : E \hookrightarrow \End(V)$ and $\rho' : T \rightarrow T_E$ for which $\rho = \rho''\circ\rho'$.
-
 \begin{proposition} \label{prop:etale-construction}

### 2014-06-27 Paper.tex
Changes at CNTA

@@
 \DeclareMathOperator{\SL}{SL}
+\DeclareMathOperator{\Sp}{Sp}
+\DeclareMathOperator{\SO}{SO}
+\DeclareMathOperator{\U}{U}
+\DeclareMathOperator{\SU}{SU}
 
@@
 TODO book of involutions 29.20 says this is trivial.
-TODO --- Find reference for this ----
 
@@
 
-\subsection{From Unitary Groups to Orthogonal Groups}
+\section{Classifying Tori in Classical Groups}
+%\section{\'Etale Algebras associated to Tori in Algebra Groups}
 
-In many cases unitary groups can be embedded into orthogonal groups, we shall only be making explicit use of this in the case where groups are associated to Hermitian and symmetric forms, however we present the more general situation.
+\TODO{Edit section to align with the following goal}
 
-Fix the following data:
-\begin{itemize}
-\item An quadratic \'etale algebra $E$ over $K$ with involution $\sigma_E$.
-\item A quaternion algebra $A_0$ over $K$ with standard involution $\sigma_{A_0}$, then define $A = A_0\otimes_K E$ with an involution of the second kind $\sigma_A = \sigma_{A_0} \otimes \sigma_E$.
-(Note that all such $A$ arise uniquely this way see \cite[2.22]{TODO - book of involutions}).
-\item An element $J\in F^\sigma$ of norm $\delta$ whose minimal polynomial at a real place $\nu$ of $K$ which ramifies in $E$ has $r_\nu$ positive roots and $s_\nu$ negative roots.
-\end{itemize}
-Then define then $SU$ to be the associated unitary group whose points over a $K$-algebra $R$ are given by:
-\[ SU_J(R) = \{ g\in (A\otimes_K R)^\times \mid \sigma_A(g)Jg = J \text{ and } Nm(g) = 1 \}. \]
-
-Now, fix a $K$-division algebra $B$ with a fixed embedding of $E$ into $B$.
-Denote the standard involution on $B$ by $\sigma_{B}$ and define an orthogonal involution by $\tau_B(x) = y\sigma(x)y^{-1}$, where $y\in E$ has $\sigma_B(y) = -y$.
-
-Now define the algebra $C = A_0 \otimes_K B$, the involution $\sigma_C = \sigma_{A_0} \otimes \sigma_B$ is the standard involution and the involution $\tau_C = \sigma_{A_0} \otimes \tau_B$ is an orthogonal involution.
-Both $\sigma_C$ and $\tau_C$ restrict to $\sigma_A$ on the embedded image of $A$ in $C$.
-
-We may thus define the group schemes $SO_J$ and $SP$:
-\[ SO_J(R) =  \{ g\in (M_{n}(C) \otimes_K R)^\times \mid \tau_C(g^t)Jg = J  \} \]
-and
-\[ SP(R) =  \{ g\in (M_{n}(C) \otimes_K R)^\times \mid \sigma_C(g^t)Jg = J  \}. \]
-We redilly observe that $SU_J$ embedds naturally into both of these groups.
-\begin{remark}
-The group $SP$ is a symplectic group, its isomorphism class does not depend on $J$.
-\end{remark}
-
-\begin{remark}
-In the special case where $A_0$ and $B$ are split, so that $SU_J$ is the special unitary group of an $E$-valued Hermitian form $H$ associated to $J$ then
-$SO_J$ is the orthogonal group associated to the $K$-valued bilinear form $B(z_1,z_2) = \Tr_{E/K}(H(z_1,z_2))$ and the group $SP$ is the symplectic group associated to the symplectic form $S(z_1,z_2) = \Tr_{E/K}(H(yz_1,z_2))$.
-
-Note that given $SO_J$ or $SP$, and the $E$-module structure on the standard representations, the group $SU_J$ may be recovered.
-Note also that $U_J = SO_J \cap SP$.
-\end{remark}
-
-\section{\'Etale Algebras  associated to Tori in Algebra Groups}
+In this section we describe maximal tori in classical groups in terms of \'etale algebras with involutions.
 
@@
 
-\subsection{Tori in Algebraic Groups}
+\subsection{Tori in algebraic groups}
 
@@
 
-\section{Forms preserved by $T_{E,\sigma}$}
+\subsection{Intrinsic properties of these tori}
 
-\subsection{Shape of the Forms}
+\subsubsection{Anisotropic}
+
+\begin{proposition}
+The torus $T_{E,\sigma}$ is anisotropic if all the field factors of $E$ are $\sigma$-stable.
+\end{proposition}
+\begin{proof}
+\TODO-
+That the condition is necissary is reasonably clear, sufficiency is less obvious.
+\end{proof}
+
+\begin{example}
+Consider $E = A \times A$ where $\sigma$ acts on each factor.
+This has the structure of an $A$ algebra, where $\sigma$ restricts to $\sigma$, by the inclusion $A\hookrightarrow A\times A$:
+\[ a \mapsto (a,a) \]
+The torus $T_{E,\sigma}$ is anisotropic.
+
+\bigskip
+Consider $E = A \times A$ where $\sigma$ acts to interchange factors.
+Give this the structure of an $A$ algebra, where $\sigma$ restricts to $\sigma$, by the inclusion $A\hookrightarrow A\times A$:
+\[ a \mapsto (a,\sigma(a)) \]
+The torus $T_{E,\sigma}$ is not anisotropic.
+\end{example}
+
+\subsubsection{Unramified}
+
+\begin{proposition}
+The torus $T_{E,\sigma}$ is unramified if all the field factors of $E$ are unramified
+\end{proposition}
+\begin{proof}
+\TODO-
+\end{proof}
+
+\subsubsection{``Relatively'' unramified}
+
+Your special unramifiedness when $A/K$ was ramified.
+
+\section{Classical groups containing a fixed torus}
+
+For each torus constructed in the previous section, we describe into which classical groups it embeds.  We also describe the conjugacy classes of embeddings, both stably and rationally.
+
+\subsection{Constructing bilinear forms from tori}
 
@@
 
-\subsection{Invariants of Hermitian Forms}
+\subsection{Invariants of the bilinear forms}
 
@@
 
-\subsection{Existence of Forms}
+\subsection{Embedding in different forms}
 
@@
 \[ H \simeq H_{E,\sigma,\lambda} \]
-if and only if there exists $\lambda_\fp$ for all localizations $\fp$ of $K$ (both archimedian and non-archimedian).
+if and only if there exists $\lambda_\fp$ for all localizations $\fp$ of $K$ (both archimedean and non-archimedean).
 \end{theorem}
@@
 where the compositions of the horizontal maps are injective.
-We must show that an element in $K^\times/N_{A/K}(A^\times) $ is in the image of the left verticle map, provided its image is in the image of the right hand verticle map.
+We must show that an element in $K^\times/N_{A/K}(A^\times) $ is in the image of the left vertical map, provided its image is in the image of the right hand vertical map.
 We must do this in spite of the fact that the horizontal maps are not surjective.
@@
 \begin{theorem}
-\TODO - summarize a pure global existance statement.
+\TODO{summarize a pure global existence statement.}
 \end{theorem}
@@
 \begin{remark}
-\TODO - Can phrase this as: The reflex algebra splits the even clifford algebra + signature conditions.
-Is there a meaningfull interpretation of the clifford algebra in this context?
-Can we interpret it as telling us about a quaternioninc symplectic group embedding of the unitary group?
+\TODO{Can phrase this as: The reflex algebra splits the even clifford algebra + signature conditions.
+Is there a meaningful interpretation of the clifford algebra in this context?
+Can we interpret it as telling us about a quaternionic symplectic group embedding of the unitary group?}
 \end{remark}
 
-\subsection{Classification of Tori in Unitary Groups}
+\subsection{Rational Conjugacy of Tori}
 
@@
 
-Let $(E,M_n,\tilde{\tau})$ be the triple consisting of $E$, the matrix algebra of degree $n$ over $E$, and an involution $\tilde{\tau}$ of disciminant $\delta_{\tau}$ so that $U_{E,A,\tau}$ is the unitary group for the $E$-Hermitian space of discriminant $\delta_{\tau}$.
+Let $(E,M_n,\tilde{\tau})$ be the triple consisting of $E$, the matrix algebra of degree $n$ over $E$, and an involution $\tilde{\tau}$ of discriminant $\delta_{\tau}$ so that $U_{E,A,\tau}$ is the unitary group for the $E$-Hermitian space of discriminant $\delta_{\tau}$.
 
-The rational conjugacty classes of maximal tori in $U_{E,A,\tau}$ are naturally identified with a subset of those of $U_{E,M_n,\tilde{\tau}}$.
-The tori in $U_{E,M_n,\tilde{\tau}}$ are assicated to triples $(F,\sigma,\lambda)$, the rational conjugacy classes of tori in $U_{E,A,\tau}$ are precisely the subset for which $(F,\sigma)\hookrightarrow (A,\tau)$, equivalently, the subset for which $F$ splits $A$.
+The rational conjugacy classes of maximal tori in $U_{E,A,\tau}$ are naturally identified with a subset of those of $U_{E,M_n,\tilde{\tau}}$.
+The tori in $U_{E,M_n,\tilde{\tau}}$ are associated to triples $(F,\sigma,\lambda)$, the rational conjugacy classes of tori in $U_{E,A,\tau}$ are precisely the subset for which $(F,\sigma)\hookrightarrow (A,\tau)$, equivalently, the subset for which $F$ splits $A$.
 
-The tori associated to $(F,\sigma,\lambda)$ in $U_{E,A,\tau}$ is the same as that in $U_{E,M_n,\tilde{\tau}}$ in particular they are $T_{F,\sigma}$, fixing an embedding $\rho : F \rightarrow A$, and an involution $\hat\tau$ of disciminant $1$ the conjugacy classes correspond to the image of $T_{F,\sigma}$ in $U_{E,A,\tau} \subset A$ where $U_{E,A,\tau}$ is defined comes from $\tau(x) = \rho(\lambda^{-1})\hat\tau(x)\rho(\lambda)$.
+The tori associated to $(F,\sigma,\lambda)$ in $U_{E,A,\tau}$ is the same as that in $U_{E,M_n,\tilde{\tau}}$ in particular they are $T_{F,\sigma}$, fixing an embedding $\rho : F \rightarrow A$, and an involution $\hat\tau$ of discriminant $1$ the conjugacy classes correspond to the image of $T_{F,\sigma}$ in $U_{E,A,\tau} \subset A$ where $U_{E,A,\tau}$ is defined comes from $\tau(x) = \rho(\lambda^{-1})\hat\tau(x)\rho(\lambda)$.
 
@@
 
-Local existance -> global existance is easy, as $\lambda \in F$ places $\lambda \in A$ so as to allow us to define the involution, which has the correct local invariants and thus gives the correct unitary group.
+Local existence $\to$ global existence is easy, as $\lambda \in F$ places $\lambda \in A$ so as to allow us to define the involution, which has the correct local invariants and thus gives the correct unitary group.
 
@@
 
-\section{Properties of $T_{E,\sigma}$}
+\section{Embeddings of unitary groups in symplectic and orthogonal groups}
 
-\subsection{Anisotropic}
+\begin{itemize}
+\item When does $\U_n$ embed into $\SO_{2n}$, $\SO_{2n+1}$ and $\Sp_{2n}$.
+\item Which tori in $\SO_m / \Sp_{2n}$ are in the images these embeddings.
+\item What are the rational conjugacy classes of these embeddings, and how do the rational conjugacy classes of tori break up?
+\item Do different inner forms embed into the same place?  What is the intersection?
 
-\begin{proposition}
-The torus $T_{E,\sigma}$ is anisotropic if all the field factors of $E$ are $\sigma$-stable.
-\end{proposition}
-\begin{proof}
-\TODO-
-That the condition is necissary is reasonably clear, sufficiency is less obvious.
-\end{proof}
+if K is non-split then the Hasse invariant of the resulting orthogonal group depends on isomorphism class of Hermitian space and thus they don't embed into the same group.
 
-\begin{example}
-Consider $E = A \times A$ where $\sigma$ acts on each factor.
-This has the structure of an $A$ algebra, where $\sigma$ restricts to $\sigma$, by the inclusion $A\hookrightarrow A\times A$:
-\[ a \mapsto (a,a) \]
-The torus $T_{E,\sigma}$ is anisotropic.
+If K is split, then the resulting orthogonal space is determined entirely by the choice of quaternion algebra (split/ramified) for the construction of the unitary group.
+We obtain different orthogonal groups in the 2 cases.
+\TODO{check how many orthogonal group isomorphism classes in this case}
 
-\bigskip
-Consider $E = A \times A$ where $\sigma$ acts to interchange factors.
-Give this the structure of an $A$ algebra, where $\sigma$ restricts to $\sigma$, by the inclusion $A\hookrightarrow A\times A$:
-\[ a \mapsto (a,\sigma(a)) \]
-The torus $T_{E,\sigma}$ is not anisotropic.
-\end{example}
+Thus there is no intersection.
 
-\subsection{Unramified}
+\item Can we understand tori in adjoint forms (earlier section).  For $\SO$ and $\Sp$ you quotient by $\pm 1$ while for $\U_n$ you quotient by $\U_1$.  Describe these as subtori instead of quotients.
+\end{itemize}
 
-\begin{proposition}
-The torus $T_{E,\sigma}$ is unramified if all the field factors of $E$ are unramified
-\end{proposition}
-\begin{proof}
-\TODO-
-\end{proof}
+\subsection{From Unitary Groups to Orthogonal Groups}
 
-\subsection{``Relatively'' Unramified}
+In many cases unitary groups can be embedded into orthogonal groups, we shall only be making explicit use of this in the case where groups are associated to Hermitian and symmetric forms, however we present the more general situation.
 
-Your special unramifiedness when $A/K$ was ramified.
+Fix the following data:
+\begin{itemize}
+\item An quadratic \'etale algebra $E$ over $K$ with involution $\sigma_E$.
+\item A quaternion algebra $A_0$ over $K$ with standard involution $\sigma_{A_0}$, then define $A = A_0\otimes_K E$ with an involution of the second kind $\sigma_A = \sigma_{A_0} \otimes \sigma_E$.
+(Note that all such $A$ arise uniquely this way see \cite[2.22]{TODO - book of involutions}).
+\item An element $J\in F^\sigma$ of norm $\delta$ whose minimal polynomial at a real place $\nu$ of $K$ which ramifies in $E$ has $r_\nu$ positive roots and $s_\nu$ negative roots.
+\end{itemize}
+Then define then $SU$ to be the associated unitary group whose points over a $K$-algebra $R$ are given by:
+\[ SU_J(R) = \{ g\in (A\otimes_K R)^\times \mid \sigma_A(g)Jg = J \text{ and } Nm(g) = 1 \}. \]
 
-\section{The Building of the Unitary Group}
+Now, fix a $K$-division algebra $B$ with a fixed embedding of $E$ into $B$.
+Denote the standard involution on $B$ by $\sigma_{B}$ and define an orthogonal involution by $\tau_B(x) = y\sigma(x)y^{-1}$, where $y\in E$ has $\sigma_B(y) = -y$.
 
-\subsection{The reduction of $T_{E,\sigma}$}
+Now define the algebra $C = A_0 \otimes_K B$, the involution $\sigma_C = \sigma_{A_0} \otimes \sigma_B$ is the standard involution and the involution $\tau_C = \sigma_{A_0} \otimes \tau_B$ is an orthogonal involution.
+Both $\sigma_C$ and $\tau_C$ restrict to $\sigma_A$ on the embedded image of $A$ in $C$.
+
+We may thus define the group schemes $SO_J$ and $SP$:
+\[ SO_J(R) =  \{ g\in (M_{n}(C) \otimes_K R)^\times \mid \tau_C(g^t)Jg = J  \} \]
+and
+\[ SP(R) =  \{ g\in (M_{n}(C) \otimes_K R)^\times \mid \sigma_C(g^t)Jg = J  \}. \]
+We readilly observe that $SU_J$ embeds naturally into both of these groups.
+\begin{remark}
+The group $SP$ is a symplectic group, its isomorphism class does not depend on $J$.
+\end{remark}
+
+\begin{remark}
+In the special case where $A_0$ and $B$ are split, so that $SU_J$ is the special unitary group of an $E$-valued Hermitian form $H$ associated to $J$ then
+$SO_J$ is the orthogonal group associated to the $K$-valued bilinear form $B(z_1,z_2) = \Tr_{E/K}(H(z_1,z_2))$ and the group $SP$ is the symplectic group associated to the symplectic form $S(z_1,z_2) = \Tr_{E/K}(H(yz_1,z_2))$.
+
+Note that given $SO_J$ or $SP$, and the $E$-module structure on the standard representations, the group $SU_J$ may be recovered.
+Note also that $U_J = SO_J \cap SP$.
+\end{remark}
 
@@
 
-\section{Embeddings of unitary groups in symplectic and orthogonal groups}
-
-\begin{theorem}
-Suppose $H$ is a Hermitian space
-\end{theorem}
-
 \end{document}

### 2014-06-30 Paper.tex
Describe Clifford Algebra for General Orthogonal Groups

@@
 \DeclareMathOperator{\SU}{SU}
+\DeclareMathOperator{\Clif}{Cliff}
 
@@
 \TODO{Hasse Principle} The map from Global to local is injective.
+
 \TODO{Simply Connected Local Fields Thing} $H^1(G)$ is trivial if $G$ simply connected at a non-real local field
+
 \TODO{Simply connected real fields results} I feel someone has given an interpretation in terms of "indexes" of groups...
@@
 \TODO{H1 classifies torsors}
+
 \TODO{remarks re twisting}
+
 \TODO{H1 and H2 for relevant tori, restrictions of scalars and norms} (possibly in a later section?)
@@
 
-When $A$ is a quaternion algebra, the analysis proceeds as above, and we may still associate to $G$ a discriminant, a central simple algebra (which is $2$-torsion if $n$ is even, and $4$-torsion when $n$ is odd) and signature information.
-As we shall not need it in the sequel, we omit the details, but remark that among other simplifications, $J$ can be taken to be diagonal, and the diagonal entries can be rescaled by $(K^\times)^2$
+More generally we may describe this as follows.
+
+Denote by $G^{\rm sc}$ and $G^{\rm ad}$ the simply connected and adjoint groups associated to $G$ and by $\pi_1(G^{\rm ad})$ the fundamental group of $G^{\rm sc}$ over $G^{\rm ad}$.
+Note that over the algebraic closure $\pi_1(G)$ is cyclic of order $4$ when $n$ is odd, and $(\ZZ/2\ZZ)^2$ if $n$ is odd.
+
+\TODO{get reference for exact form of $\pi_1(G)$}
+
+The map:
+\[ H^1(\GalKbK, \Aut(G)) \rightarrow H^1(\GalKbK, \pi_0(\Aut(G))) \]
+associates to a form a $G$ a discriminant, that is, a quadratic \'etale algebra $D(G)$.
+The map:
+\[ H^1(\GalKbK, G^{\rm ad}) \rightarrow H^1(\GalKbK, \pi_1(G^{\rm ad})) \]
+associates to $G$ an element of the brauer group $Br(D(G))$ which we call the (class of the) Clifford algebra.
+Based on our understanding of $ \pi_1(G^{\rm ad})$ we observe that the Clifford algebra is an algebra with an involution. 
+This involution is of the second kind if $n$ is odd, is orthogonal if $n \cong 0 \pmod{4}$ and symplectic otherwise.
+Finally, the associated class in:
+\[  H^1(\GalKbK, G^{\rm sc}),  \]
+which is supported at the real places of $K$, is the index.
+
+A more careful analysis allows us to deduce the following detailed structure theorem for the Clifford algebra over local fields.
+We remark that the following characterization allows one to recover the algebra $(A,\tau)$ from $[\Clif^+_{A,\tau}]$.
+\begin{itemize}
+\item If $n$ is even, $A$ is a matrix algebra, and the discriminant is non-trivial, then class of $[\Clif^+_{A,\tau}]$ is trivial.
+\item If $n$ is even, $A$ is not a matrix algebra, and the discriminant is non-trivial then $[\Clif^+_{A,\tau}]$ is non-trivial.
+\item If $n$ is even, $A$ is a matrix algebra, and the discriminant is trivial, then class of $[\Clif^+_{A,\tau}]$ is a direct sum of two isomorphic algebras, their trivialitity depends on the choice of $\tau$.
+\item If $n$ is even, $A$ is not a matrix algebra, and the discriminant is trivial then $[\Clif^+_{A,\tau}]$ is a direct sum of two non-isomorphic algebras in the $2$-torsion of the Brauer group, the isomorphism over the center depends on the choice of $\tau$, note that the isomorphism class over $k$ does not.
+
+\item If $n$ is odd, $A$ is a matrix algebra, and the discriminant is non-trivial, then class of $[\Clif^+_{A,\tau}]$ is trivial.
+\item If $n$ is odd, $A$ is not a matrix algebra, and the discriminant is non-trivial then $[\Clif^+_{A,\tau}]$ is trivial.
+\item If $n$ is odd, $A$ is a matrix algebra, and the discriminant is trivial, then class of $[\Clif^+_{A,\tau}]$ is a direct sum of two isomorphic algebras in the $2$-torsion of the Brauer group, their trivialitity depends on the choice of $\tau$.
+\item If $n$ is odd, $A$ is not a matrix algebra, and the discriminant is trivial then $[\Clif^+_{A,\tau}]$ is a direct sum of two non-isomorphic algebras which are $4$-torsion, the isomorphism over the center depends on the choice of $\tau$, note that the isomorphism class over $k$ does not.
+\end{itemize}
+See \cite[Thm 9.12]{book_of_involutions}.
+
+The structure over a global field can then be deduced from this, as the global structure is determined by the local structure.
 \end{remark}

### 2014-07-02 Paper.tex
Explain role of "\lambda" for algebras with involution
Explain analog of importance of lambda in Tr(\lambda x\sigma(y)) for
algebras with involution

@@
 All the non-degenerate symmetric bilinear forms on $E$ are of the form:
-\[ Tr_{E/K}(\lambda x\sigma(y) \]
+\[ Tr_{E/K}(\lambda x\sigma(y)) \]
 All the non-degenerate Hermitan forms on $E$ are of the form:
-\[ Tr_{E/A}(\lambda x\sigma(y) \]
+\[ Tr_{E/A}(\lambda x\sigma(y)) \]
 where $\lambda \in E^\sigma$ is a unit.
@@
 \end{corollary}
+
+\subsubsection{Algebra's with involutions}
+
+\begin{theorem}
+Let $A$ be a central simple algebra over $K$.
+Let $E$ be an \'etale algebra over $k$ which embeds into $A$ as a maximal \'etale subalgebra.
+Suppose $\tau_1,\tau_2$ are two involutions on $A$ which preserve $E$ and such that $\tau_1|_E = \tau_2|_E$ then:
+\[ \tau_1 = {\rm Int}_\lambda\circ\tau_2 \]
+for some $\lambda \in E^\times$.
+\end{theorem}
+\begin{proof}
+Via the classification of involutions on $A$
+\TODO{cite book of involutions or above}
+ we know $\tau_1 = {\rm Int}_\lambda\circ\tau_2$ for $\lambda \in A^\times$.
+
+However, since $\tau_1$ and $\tau_2$ both preserve $E$ it follows that ${\rm Int}_\lambda$ must preserve $E$ and thus at least normalize $E$.
+Moreover, as $\tau_1|_E = \tau_2|_E$ we find that ${\rm Int}_\lambda$ acts trivially on $E$ and thus $\lambda$ centralizes $E$. We conclude that $\lambda\in E$ by checking over the algebraic closure.
+\end{proof}
+
+\begin{theorem}
+If the involutions $\tau_1$ and $\tau_2$ are both orthogonal or both Hermitian then $\sigma(\lambda) = \lambda$.
+
+If one of $\tau_1$ is simplectic, the other orthogonal, then $\sigma(\lambda) = -\lambda$.
+\end{theorem}
+
+\begin{corollary}
+Fixing any one involution $\tau$ on $A$ (either orthogonal or Hermitian) preserving $E$.
+All of the involutions on $A$ preserving $E$ are of the form:
+\[ {\rm Int}_\lambda\circ\tau \]
+where $\lambda \in (E^\sigma)\times$.
+\end{corollary}
+
+\begin{theorem}
+Let $A$ be a central simple algebra over $K$.
+Let $E$ be an \'etale algebra over $k$ which embeds into $A$ as a maximal \'etale subalgebra.
+Let $\rho_1,\rho_2 : E\hookrightarrow A$ be two embeddings.
+
+There exists $\gamma \in A^\times$ such that $\rho_1 = {\rm Int}_\gamma\rho_2$.
+\end{theorem}
+\begin{proof}[Sketch]
+\TODO{Complete the sketch}
+
+Let $g\in A \otimes_k \overline{k}$ realize ${\rm Int}_g\rho_2$.
+
+"It is well known" that this exists over the algebraic closure.
+  - It is well known that we can conjugate so that the images are equal, that we can obtain the isomorphism on the nose is the fact that weil group is big.
+
+We can verify then that $g\sigma(g^{-1})$ gives an element of $E^\times$.
+Thus $g\sigma(g^{-1}) = e\sigma(e^{-1})$ for $e\in E^\times$ (by Hilbert's 90) so that $ge^{-1}$ is a galois stable element realizing the isomorphism.
+\end{proof}
+
+\begin{remark}
+The importance of the above theorem is that it allows us to interchange the following two problems:
+\begin{enumerate}
+\item Understand rational conjugacy classes of maps $\rho: (E,\sigma) \hookrightarrow (A,\tau)$
+\item Understand the rational conjugacy classes of $\tau$ on $A$ extending $\sigma$ on $E$ with respect to a fixed embedding $E\hookrightarrow A$.
+\end{enumerate}
+By the above corralary \ref{TODO} this amounts to a thorough understanding of the rational conjugacy classes of the involutions $\tau_\lambda =  {\rm Int}_\lambda\circ\tau$.
+
+\TODO{at some point need to explain why $\tau_\lambda$ and $\tau$ are not rationally conjugate}
+Key point is that $\tau(\lambda x \lambda^{-1}) = \tau(\lambda^{-1}) \tau(x) \tau(\lambda)$ so the involutions $\tau$ and ${\rm Int}_{\tau(\lambda)}\circ \tau\circ {\rm Int}_\lambda$ are rationally conjugate.
+\end{remark}
 

### 2014-07-03 Paper.tex
Add some more explicit TODO's and proof sketches

@@
 
+\subsection{Alternating Forms}
+
+As above, but define classical simplectic groups.
+
+Fix a free $K$-module $V$ of dimension $2n$. There is a unique a non-degenerate alternating $K$-valued $K$-bilinear pairing $S$ on $V$.
+
+$\Sp_S = \Sp = \Aut(V,S)$.
+
+The forms of $(V,S)$ are in bijection with $H^1(\GalKbK, \Aut(V,S))$, as there is only a unique form, this cohomology group vanishes.
+
+\subsection{Symplectic Groups}
+
+For the purpose of this paper a symplectic group means a simply connected group of type $C_n$.
+The outer automorphism group of such a group is trivial, the center if $\mu_2$.
+
+We may construct the symplectic groups as defined above as follows.
+Fix a quaternion algebra $A$ over $K$ (we allow $M_2(K)$) together with the standard quaternionic involution $\sigma$.
+If $A$ is $M_2(K)$ then $\sigma( \left( \begin{smallmatrix} w & x\\ y & z \end{smallmatrix} \right) ) =\left( \begin{smallmatrix}z & {-x}\\ {-y} & w \end{smallmatrix} \right) $
+
+Define then $G$ to be the group scheme whose points over a $K$-algebra $R$ are given by:
+\[ G(R) = \{ g\in (M_{n}(A) \otimes_K R)^\times \mid \tau(g^t)g = 1_n \}. \]
+We remark the involution $\tau(g^t)$ on $M_{n}(A)$ is of symplectic type.
+
+\begin{theorem}
+All forms of $G$ arise this way.
+\end{theorem}
+\cite[TODO]{book of involutions}
+
+The cohomological interpretation of this result is as follows:
+
+As the outer automorphism group was trivial and the center was $\mu_2$ we obtain the exact sequence:
+\[\ldots \rightarrow H^1(\GalKbK,\mu_2) \rightarrow  H^1(\GalKbK,G)  \rightarrow  H^1(\GalKbK, \Aut(G)) \rightarrow  H^2(\GalKbK, \mu_2)  \]
+We may thus associate to $G$ a quaternion algebra $A$.
+The cohomology set $H^1(\GalKbK,G) $ classifies alternating forms on $A^n$, as above there is a unique such and so this cohomology set is trivial.
+\cite[TODO]{book of involutions}.
+
 \section{Classifying Tori in Classical Groups}
@@
 
-\subsubsection{Algebra's with involutions}
+\subsubsection{Algebras with involutions}
 
@@
 \subsection{Invariants of the bilinear forms}
+
+From the above it is clear that to classify the groups $G$ into which $T_{E,\sigma}$ embeds, we must understand which forms may arise as one of
+\[ H_{E,\sigma,\lambda} := \tfrac{1}{2}Tr_{E/A}\left(\lambda x\sigma(y)\right) \]
+for Hermitian forms or:
+\[ B_{E,\sigma,\lambda} := \tfrac{1}{2}Tr_{E/K}\left(\lambda x\sigma(y)\right) \]
+for Bilinear forms.
+In particular, we must understand the invariants of these forms.
 
@@
 
+\subsubsection{Algebras with involutions}
+
+We now  explain how the invariants of $\tau_\lambda$ depend on $\lambda$.
+Note that in this case the choice of ``base point" is not as canonical and the collection of involutions is really a torsor under the action of the appropriate unit group.
+
+\TODO{fill in details}
+\begin{itemize}
+\item $\lambda$ choses discriminant of unitary groups.
+\subitem This should be intrinsicly clear from definitions... hopefully
+\TODO{In the above version I relate the unitary and orthogonal cases... not clear I want to do that for this case until we give construction later}
+\item $\lambda$ choses the Clifford invariant and index of orthogonal groups.
+\subitem (Same formula as other case)
+\item $\lambda$ irrelevent for symplectic groups.
+\end{itemize}
+
 \subsection{Embedding in different forms}
@@
 
+\subsubsection{Unitary Groups}
+
 \begin{theorem}
@@
 The exact sequence $H^1(F) \rightarrow H^1(Aut(A,F)) \rightarrow H^1(Aut(F))$ tells us these are all conjugate.
-A direct argument of this claim would be nice.
-(Conjugacy of maximal \'etale sub-algebras of central simple algebras must be known).
+\TODO{cite above for direct argument of this claim}
 
@@
 
+\TODO{cohomological interpretation is supposed to be later I think}
 \begin{remark}
@@
 \end{remark}
+
+\subsubsection{Orthgogonal Groups}
+
+\TODO{copy and paste from that other thing where I wrote the general theorem}
+The only meaningful way in which the argument differs from my paper is a semi-ugly case analysis on the clifford algebras.
+
+\TODO{cohomological interpretation is later I think}
+
+\subsubsection{Symplectic Groups}
+
+\TODO{write down the result}
+
+\TODO{cohomological interpretation is later I think}
 
@@
 
-We may thus define the group schemes $SO_J$ and $SP$:
-\[ SO_J(R) =  \{ g\in (M_{n}(C) \otimes_K R)^\times \mid \tau_C(g^t)Jg = J  \} \]
+We may thus define the group schemes $\SO_J$ and $\Sp$:
+\[ \SO_J(R) =  \{ g\in (M_{n}(C) \otimes_K R)^\times \mid \tau_C(g^t)Jg = J  \} \]
 and
-\[ SP(R) =  \{ g\in (M_{n}(C) \otimes_K R)^\times \mid \sigma_C(g^t)Jg = J  \}. \]
+\[ \Sp(R) =  \{ g\in (M_{n}(C) \otimes_K R)^\times \mid \sigma_C(g^t)Jg = J  \}. \]
 We readilly observe that $SU_J$ embeds naturally into both of these groups.
@@
 \begin{remark}
-In the special case where $A_0$ and $B$ are split, so that $SU_J$ is the special unitary group of an $E$-valued Hermitian form $H$ associated to $J$ then
+In the special case where $A_0$ and $B$ are split, so that $\SU_J$ is the special unitary group of an $E$-valued Hermitian form $H$ associated to $J$ then
 $SO_J$ is the orthogonal group associated to the $K$-valued bilinear form $B(z_1,z_2) = \Tr_{E/K}(H(z_1,z_2))$ and the group $SP$ is the symplectic group associated to the symplectic form $S(z_1,z_2) = \Tr_{E/K}(H(yz_1,z_2))$.
 
-Note that given $SO_J$ or $SP$, and the $E$-module structure on the standard representations, the group $SU_J$ may be recovered.
-Note also that $U_J = SO_J \cap SP$.
-\end{remark}
+Note that given $\SO_J$ or $\Sp$, and the $E$-module structure on the standard representations, the group $\SU_J$ may be recovered.
+Note also that $U_J = \SO_J \cap \Sp$.
+\end{remark}
+
+\TODO{prove that this construction is universal - sketch follows}
+\begin{itemize}
+\item It suffices to prove that rational conjugacy is the same as rational isomorphism.
+\item First claim any conjugate embedding (of groups) arises from a conjugate embedding (of algebras with involutions).
+\item We want to show that any two embeddings $A \hookrightarrow C$ are conjugate.
+        With $A,C$ as defined above but the embedding not necissarily coming from the condition.
+
+        NOTE: we only really care about showing they are $C$ conjugate whenever they are $C\otimes_k \overline{k}$ conjugate.
+\item Pretty sure that $A$ is the centralizer in $C$ of the center of $A$.
+\item Thus, conjugacy classes of $A$ equivalent to conjugacy classes of center of $A$.
+\item Conjugacy classes of the center $Z(A)$ of $A$ are equivalent to $Z(A)$ module structures on the "representation" space of $C$ that are "compatible" with a 
+         $[C]$-module structure on the space.
+
+          That is, there is an $[C]$-basis $c_1,\ldots c_n$ of the representation space, such that $Z(A) \cdot c_i \subset [C]\cdot c_i$.
+          This should follow from the fact that $Z(A)$ splits $C$.
+\item All $[C]$-module structures on the space are equivalent (Hilberts 90), so that any two $c_i$ basis are $C$ equivalent.
+\item This reduces us to conjugacy of $Z(A)$ inside $[C]$, which we have previously shown, but is also well known for quaternion algebras.
+\end{itemize}
+
+\TODO{Want to prove the following facts [that one hopes are facts]}
+\begin{itemize}
+\item The normalizer in $\Sp$ (resp. $\SO$) of $\U$ is $\mu_2 \rtimes \U$ (resp. $\U$).  [or something like this]
+\subitem  suffices to check over the algebraic closure.
+\item The centralizer of the center of $\U$ in $\Sp$ and $\SO$ is $\U$
+\subitem suffices to check over the algebraic closure.
+\subitem Note that the connected component of the normalizer of the center of $\U$ is the centralizer of the center.
+              (first claim reduces to second + claim that normalizer is connected in $\SO$ case)
+\end{itemize}
+
+\TODO{Invariants of orthogonal from those of unitary}
+\begin{itemize}
+\item The discriminant of the unitary involution should determine clifford of the orthogonal.
+\item The discriminant of the orthogonal should be determined by the choice of $E$.
+\item The index of the unitary and orthogonal should be the same.
+\end{itemize}
+
+\TODO{Summary - Given orthogonal which unitary are possible}
+\TODO{Summary - Given unitary which orthogonal are possible}
+
+\TODO{cohomological reinterpretation is now or later?}
+
+\subsection{Decomposing Conjugacy Classes of Tori}
+
+\TODO{The questions about which tori are in the image}
+
+\TODO{cohomological reinterpretation is now or later?}
 

### 2014-07-18 Paper.tex
Add more sketches of proofs

@@
 Fix a free $K$-module $V$ of dimension $2n$. There is a unique a non-degenerate alternating $K$-valued $K$-bilinear pairing $S$ on $V$.
-
-$\Sp_S = \Sp = \Aut(V,S)$.
-
+We define the associated symplectic group to be $\Sp_S = \Sp = \Aut(V,S)$.
 The forms of $(V,S)$ are in bijection with $H^1(\GalKbK, \Aut(V,S))$, as there is only a unique form, this cohomology group vanishes.
@@
 For the purpose of this paper a symplectic group means a simply connected group of type $C_n$.
-The outer automorphism group of such a group is trivial, the center if $\mu_2$.
-
-We may construct the symplectic groups as defined above as follows.
+The outer automorphism group of such a group is trivial, the center is $\mu_2$.
+
+We may construct these symplectic groups as follows.
 Fix a quaternion algebra $A$ over $K$ (we allow $M_2(K)$) together with the standard quaternionic involution $\sigma$.
@@
 
+\TODO{Theorem expessing the $E$ splits $M$ condition}
+
 We now  explain how the invariants of $\tau_\lambda$ depend on $\lambda$.
@@
 
-\TODO{prove that this construction is universal - sketch follows}
-\begin{itemize}
-\item It suffices to prove that rational conjugacy is the same as rational isomorphism.
+\begin{theorem}
+Let $(A,\tau_A)$ be a central simple algebra of degree $n$ over $(E,\sigma)$ with involution of the second kind.
+Suppose $(C,\tau_C)$ is a central simple algebra of degree $n$ over $k$ with orthogonal involution.
+Then $(A,\tau_A)\hookrightarrow (C,\tau_C)$ if and only if there exists $(A_0,\tau_0)$ a central simple algebra over $k$ with syplectic involution and $(B,\tau_B)$ a quaternion algebra over $k$ with an orthogonal involution such that:
+\begin{enumerate}
+\item $(E,\sigma) \hookrightarrow (B,\tau_B)$.
+\item $(A,\tau_A) = (A_0,\tau_0) \otimes_k (E,\sigma)$.
+\item $(C,\tau_C) = (A_0,\tau_0) \otimes_k (B,\tau_B)$.
+\end{enumerate}
+\end{theorem}
+\begin{proof}
+\TODO{fill in sketch}
+
+\TODO{Note-I suspect one can turn the argument about rataional conjugacy=rational isomorphism into an alternate constructive proof}
+\begin{itemize}
+\item
+We know that $(A,\tau) = (A_0,\tau_0)\otimes (E,\sigma)$ for a unique $(A_0,\tau_0)$.
+\item
+Composition of maps then gives us an inclusion $(A_0,\tau_0) \hookrightarrow (A,\tau_A)$.
+\item
+It is then automatic that there exists $B$ such that $C= A_0 \otimes_k B$.
+\item
+Note that if $C$ split $A_0,B$ not split and $E$ split then no map $A_0\times A_0$ into $C$
+ ($GL_{A_0\times A_0}$ has no representation of dimension $2n$, smallest is dimension $2n^2$
+ this implies $E\hookrightarrow B$.
+\item
+We then can consider the restriction of $\tau_C$ to $A_0$ and $B$.
+This determines $\tau_B'$ and $\tau_0'$.
+\item
+One of $\tau_B', \tau_0'$ is syplectic the other orthogonal.
+We claim we can't get them backwords because the discriminant of $\tau_C$ would be $D(\tau_0')^2$ if we did.
+In which case it is a square, and we can easily then swap $\tau_B'$ and $\tau_0'$ roles...
+\end{itemize}
+\end{proof}
+
+\begin{proposition}
+\TODO{Rational conjugacy classes}
+Rational conjugacy is the same as rational isomorphism.
+\end{proposition}
+\begin{proof}
+\TODO{this might also be modifiable to show that the above construction is universal}
+\begin{itemize}
 \item First claim any conjugate embedding (of groups) arises from a conjugate embedding (of algebras with involutions).
@@
 \end{itemize}
+\end{proof}
 
 \TODO{Invariants of orthogonal from those of unitary}
-\begin{itemize}
+
+\begin{proposition}
+Let $(A,\tau_A)$ be a central simple algebra of degree $n$ over $(E,\sigma)$ with involution of the second kind.
+Suppose $(C,\tau_C)$ is a central simple algebra of degree $n$ over $k$ with orthogonal involution such that $(A,\tau_A)\hookrightarrow (C,\tau_C)$.
+
+The invariants of $(A,\tau_A)$ and $(C,\tau_C)$ are related as follows:
+\begin{enumerate}
+\item The discriminant of $\tau_C$ is $\delta_E^{n}$.
 \item The discriminant of the unitary involution should determine clifford of the orthogonal.
-\item The discriminant of the orthogonal should be determined by the choice of $E$.
-\item The index of the unitary and orthogonal should be the same.
-\end{itemize}
-
+\TODO{phrasing of above... }
+          changing discriminant (action of $d\in k^\times/N_{E/k}(E^\times)$ is (something like) by $(d,\delta_E)$ on class of clifford algebra.
+\item The discriminant of the unitary involution should be determined (somehow) by discriminant of $A_0$
+\TODO{Not sure if we want to say this in this proposition or a elsewhere}
+\item The algebra $B$ is determined by $A_0$ and $C$. The discriminant of $\tau_B$ should be $\delta_E$.
+
+\item The index of $\tau_A$ and $\tau_C$ are the same (or at least determine each other).
+\end{enumerate}
+\end{proposition}
+\begin{proof}
+\TODO{complete sketch}
+\begin{itemize}
+\item The first and fourth points follow from definition of discriminant (it is the norm of the appropriate element of $E$)
+\item The third point is clear by construction but the actual dependence is important.
+\item The second then follows from the third (by construction) but again, the actual dependence should be spelled out.
+\item The fifth point in one direction is clear (maximal split in torus can be pushed forward). In the other direction is clear for $A,C$ matrix algebras. 
+         Case by case analysis should cover the rest.
+\end{itemize}
+\end{proof}
+
+Based on the above we conclude:
+\begin{proposition}
 \TODO{Summary - Given orthogonal which unitary are possible}
+\begin{itemize}
+\item The index is determined.
+\item The algebra $E$ is determined when $n$ is odd.
+\item When $n$ is even, the discriminant must be trivial or there are NO unitary groups.
+\item The choice of $B$ determines $A_0$ which determines $A$.
+\item The Clifford algebra determines the discriminant of the unitary group.
+\end{itemize}
+\end{proposition}
+
+Based on the above we also conclude:
+\begin{proposition}
 \TODO{Summary - Given unitary which orthogonal are possible}
+\begin{itemize}
+\item The discriminant and index are determined. (non-trivial discriminants can never occur if $n$ is even).
+\item The Clifford algebra can vary, this depends on the choice of $B$ in the construction.
+\subitem The choice of $B$ determines $C$...
+the choice is then not really of the clifford algebra (as of $C$), which then together with the choice of discriminant of the unitary group determines the Clifford algebra.
+\subitem The interpretation of the Clifford algebra as a cohomology class in some sense depends on choice of map $E\hookrightarrow C$, which depends on $E\hookrightarrow B$.
+               The apparent difficulties of this are likely allieviated by the fact that $n$ even forces trivial discriminant!.
+
+\item The limitations on choise are that $E$ splits $B$, this limits choices for $C$.
+\end{itemize}
+\end{proposition}
+
+\TODO{same as above but for symplectic}
 
@@
 
+\begin{itemize}
+\item I think $T_{E,\sigma}$ which embeds in an orthogonal is in the image of a unitary if and only if $E$ has a quadratic subextension which $\sigma$ restricts non-trivially to.
+
+Fixing $x$ a generator of this subextension, the unitary group should come from the centralizer of this in the orthogonal group (suffices to check over algebraic closure).
+
+\item \TODO{example of an even degree field with no degree $2$ subextension - an alternating group Galois extension should work}
+
+\item Any torus in the image from a unitary group should arise from a unique rational conjugacy class of unitary group (determined by the quadratic subextension).
+
+\item I think the same is true for symplectic groups.
+
+\item Given $T_{E,\sigma}$ not sure when it embeds in both a symplectic and orthgonal (for the same algebra).
+\subitem
+             It will if it embeds into a unitary (as it is then in the intersection).
+\subitem
+             But I suspect that every torus embedding in a symptlectic (resp orthogonal) embeds in an orthogonal (resp symplectic) though likely not into all the orthogonals.
+\end{itemize}
+
 \TODO{cohomological reinterpretation is now or later?}
+   - This is largely the difference between the "weil groups" of the AN and DN/CN types.
+          (really the weyl semi direct the outer automorphism group)
+   -
 

### 2014-10-08 Paper.tex
Minor changes

@@
 
+\TODO{explicit define how to find $\delta$ (norm of an anti-symmetric element cite book of involutions)}
+
 One may check that $G$ determines $E$, $A$, $\delta$ and the signatures uniquely when $n>1$. Indeed, we may check this locally.
@@
 
+\TODO{explicit define how to find the discriminant (norm of an anti-symmetric element cite book of involutions)}
+
 The map:
 \[ H^1(\GalKbK, \Aut(G)) \rightarrow H^1(\GalKbK, \pi_0(\Aut(G))) \]
-associates to a form a $G$ a discriminant, that is, a quadratic \'etale algebra $D(G)$.
+associates to a form of $G$ a discriminant, that is, a quadratic \'etale algebra $D(G)$.
 The map:
@@
 \subsection{Embedding in different forms}
+
+\TODO{This currently only covers classical unitary case, do we want to include other classical cases/change the title a bit?}
+\TODO{could also put this under 4.4.1}
+\TODO{given what we do in 4.4.1 it is important to cover this case}
 

### 2014-10-08 Paper.tex
Add a couple more TODOs

@@
 
+\TODO{We should have a corrallary to make the above remark specific}
+\TODO{Rational conjugacy classes <-> involutions up to rational conjugacy <-> $E^\sigma/N(E)$}
+
 \subsection{Invariants of the bilinear forms}
@@
 \subsection{Rational Conjugacy of Tori}
+
+\TODO{We still never actually prove that rational conjugacy is equivalent to choice of $\lambda$}
+\TODO{We should say something back at the end of 4.1 about this}
+\TODO{In this section we just need to say which $\lambda\in E^{\sigma}/N_{E/E^\sigma}(E)$ actually give each isomorphism class and which isomorphism classes are possible}
 
